---
pagetitle: "2024 Biennial Transparency Report Projections Chapter: Tables & Figures"
output:
  html_document:
    number_sections: false
    highlight: tango
    fontsize: 12
    fig_caption: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding=encoding, 
  output_dir = here::here("output/2024_BTR1/car-tables-figs")) })
params:
  config: "config_2024"
  mode: "interactive"
---

```{r, setup, include = FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", fig.width = 9, fig.height = 7)

if ((!isTRUE(getOption('knitr.in.progress'))) | (knitr::is_html_output())) {
  ow = 1200
} else {
  ow = 600
}

knitr::opts_template$set(rtf_out = list(results = "asis", out.width = ow))
knitr::opts_template$set(img_out = list(out.width = ow))
knitr::opts_knit$set(root.dir = here::here())

library(jplots)

# Accommodate different running mode options:
# interactive: values drawn from targets cache.
# targets: updated as part of pipeline via targets::tar_make(), sent to /output folder

if(params$mode == "interactive") {
  source(here::here("scripts/packages.R"))
  devtools::load_all(here())
}

withr::with_dir(
    here::here(), {
      config <- tar_read(config_2022)
      input_dataframe <- tar_read(usproj_emissions)
      targets::tar_load(c("category_list", "aeo_evo_data", "usproj_emissions"))
      usproj_2021 <- read_csv("output/2021NCBR/usproj_emissions.csv", col_types = cols())
  })

stopifnot(exists("config"))
stopifnot(exists("category_list"))

options("usproj.category_list" = category_list)
output_root <- config$report_output_root
```


```{r}
tar_load(aeo2022)
tar_load(eiahist_em_data)
aeo_em <- aeo2022$emissions
aeo_ac <- aeo2022$activity
tar_load(br_key_variables_formatted)

# yli <- c(2005, 2010, 2015, config$base_year, 2025, 2030, 2035)
# yls <- sapply(yli, as.character)
# ylsh <- head(yls, 5)
# ylsp <- tail(yls, 4)

row_label_md_gas <- function(row_id) {
  case_when(
    row_id == "CO2" ~ "CO<sub>2</sub>",
    row_id == "CH4" ~ "CH<sub>4</sub>",
    row_id == "N2O" ~ "N<sub>2</sub>O",
    row_id == "SF6" ~ "SF<sub>6</sub>",
    row_id == "NF3" ~ "NF<sub>3</sub>",
    
    row_id == "LULUCF (hist/lowseq)" ~ "LULUCF (historical / low-sequestration)",
    row_id == "LULUCF (highseq)" ~ "LULUCF (high-sequestration)",
    
    row_id == "GrossTotal" ~ "Total Gross Emissions",
    row_id == "NetTotal" ~ "Total Net Emissions",
    TRUE ~ unclass(row_id)
  )
}

row_label_gas <- function(row_id) {
  case_when(
    row_id == "LULUCF (hist/lowseq)" ~ "LULUCF (historical / low-sequestration)",
    row_id == "LULUCF (highseq)" ~ "LULUCF (high-sequestration)",
    
    row_id == "GrossTotal" ~ "Total Gross Emissions",
    row_id == "NetTotal (hist/lowseq)" ~ "Total Net Emissions (historical / low-sequestration)",
    row_id == "NetTotal (highseq)" ~ "Total Net Emissions (high-sequestration)",

    TRUE ~ unclass(row_id)
  )
}

row_label_sector <- function(row_id) {
  case_when(
    row_id == "Energy_excl_Trans" ~ "Energy",
    row_id == "IPPU" ~ "Industrial Processes",
    
    row_id == "LULUCF (hist/lowseq)" ~ "LULUCF (historical / low-sequestration)",
    row_id == "LULUCF (highseq)" ~ "LULUCF (high-sequestration)",
    
    row_id == "GrossTotal" ~ "Total Gross Emissions",
    row_id == "NetTotal (hist/lowseq)" ~ "Total Net Emissions (historical / low-sequestration)",
    row_id == "NetTotal (highseq)" ~ "Total Net Emissions (high-sequestration)",

    TRUE ~ unclass(row_id)
  )
}

```

## Tables {.tabset}

### Table 5-1. Historical and Projected U.S. GHG Emissions Baseline, by Gas: 2005-2035 (MMT CO2e)

```{r, table_gas_summary, opts.label = "rtf_out"}

make_table_gas_summary <- function() {
  
  show_years <- c(2005, 2010, 2015, config$base_year, 2025, 2030, 2035)
  
  show_years_chr <- as.character(show_years)
  show_years_hist_chr <- as.character(show_years[show_years <= config$base_year])
  show_years_proj_chr <- as.character(show_years[show_years > config$base_year])
  
  gas_order <- c("CO2", "CH4", "N2O", "HFCs", "PFCs", "SF6", "NF3")
  
  row_id_order <- c(
    gas_order,
    "GrossTotal",
    "LULUCF (hist/lowseq)",
    "LULUCF (highseq)",
    "NetTotal (hist/lowseq)",
    "NetTotal (highseq)"
  )
  
  scen_order <- c("historical", "WM", "WM-lowseq", "WM-highseq")

  gross_by_gas <- usproj_emissions %>%
    filter(category == "GrossTotal", 
           gas %in% gas_order,
           year <= config$base_year & scenario == "historical" |
             year > config$base_year & scenario == "WM") %>%
    mutate(row_id = gas)

  gross_total <- usproj_emissions %>%
    filter(category == "GrossTotal",
           gas == "Total",
           year <= config$base_year & scenario == "historical" |
             year > config$base_year & scenario == "WM") %>%
    mutate(row_id = category)

  altscen_totals <- usproj_emissions %>%
    filter(category %in% c("LULUCF", "NetTotal"),
           gas == "Total",
           year <= config$base_year & scenario == "historical" |
             year > config$base_year & scenario %in% c("WM-lowseq", "WM-highseq")) %>%
    mutate(row_id = case_when(
      scenario %in% c("WM-lowseq", "historical") ~ glue("{category} (hist/lowseq)"),
      scenario == "WM-highseq" ~ glue("{category} (highseq)"),
      TRUE ~ NA_character_
    ))

  tab_data <- bind_rows(
    gross_by_gas,
    gross_total,
    altscen_totals
    ) %>%
    filter(year %in% show_years) %>%
    select(-scenario) %>%
    mutate(value = round(value, 1)) %>% # show 1 more decimal in change tracking than pub table
    pivot_wider(names_from = year, values_from = value) %>%
    arrange(factor(row_id, levels = row_id_order)) %>%
    mutate(row_id = row_label_gas(row_id))

  write_csv(tab_data, path(output_root, "car-tables-figs/tbl-csv/tbl_5-1_gas_summary.csv"))

  res_gt <-
    tab_data %>%
    table_basic(rowname = "row_id") %>%
    text_transform(location = cells_stub(), row_label_md_gas) %>%
    fmt_number(columns = all_of(show_years_chr), decimals = 0) %>%
    tab_spanner(label = md("Historical"), columns = all_of(show_years_hist_chr)) %>%
    tab_spanner(label = md("Projected"), columns = all_of(show_years_proj_chr)) %>%
    tab_stubhead(label = md("Gas")) %>%
    cols_hide(c(category, region, gas, unit)) %>%
    format_fake_summary_rows()

}

em_table_5_1 <- make_table_gas_summary()
table_output_wrapper(em_table_5_1, path(output_root, "car-tables-figs/tbl-png/tbl_5-1_gas_summary.png"))
```

### Table 5-2. Historical and Projected U.S. Greenhouse Gas Emissions Baseline, by Sector: 2005-2035 (MMT CO2e)


```{r, table_5_2, opts.label = "rtf_out"}

make_table_sector_summary <- function() {

  show_years <- c(2005, 2010, 2015, config$base_year, 2025, 2030, 2035)
  
  show_years_chr <- as.character(show_years)
  show_years_hist_chr <- as.character(show_years[show_years <= config$base_year])
  show_years_proj_chr <- as.character(show_years[show_years > config$base_year])
  
  sector_order <- c("Energy_excl_Trans", "Transportation", "IPPU", "Agriculture", "Waste", "LULUCF")

  row_id_order <- c(
    setdiff(sector_order, "LULUCF"),
    "GrossTotal",
    "LULUCF (hist/lowseq)",
    "LULUCF (highseq)",
    "NetTotal (hist/lowseq)",
    "NetTotal (highseq)"
  )

  sector_totals_non_lulucf <- usproj_emissions %>%
    filter(
      category %in% setdiff(sector_order, "LULUCF"),
      gas == "Total",
      year <= config$base_year & scenario == "historical" |
             year > config$base_year & scenario == "WM"
    ) %>%
    mutate(row_id = category)
  
  gross_total_non_lulucf <- sector_totals_non_lulucf %>%
    group_by(year) %>%
    mutate(value = sum(value)) %>%
    filter(category == "Agriculture") %>%
    mutate(category = "GrossTotal") %>%
    mutate(row_id = "GrossTotal")
  
  altscen_totals <- usproj_emissions %>%
    filter(category %in% c("LULUCF", "NetTotal"),
           gas == "Total",
           year <= config$base_year & scenario == "historical" |
             year > config$base_year & scenario %in% c("WM-lowseq", "WM-highseq")) %>%
    mutate(row_id = case_when(
      scenario %in% c("WM-lowseq", "historical") ~ glue("{category} (hist/lowseq)"),
      scenario == "WM-highseq" ~ glue("{category} (highseq)"),
      TRUE ~ NA_character_
    ))
  
  tab_data <- bind_rows(
    sector_totals_non_lulucf,
    gross_total_non_lulucf,
    altscen_totals
    ) %>%
    filter(year %in% show_years) %>%
    select(-scenario) %>%
    mutate(value = round(value, 1)) %>% # show 1 more decimal in change tracking than pub table
    pivot_wider(names_from = year, values_from = value) %>%
    arrange(factor(row_id, levels = row_id_order)) %>%
    mutate(row_id = row_label_sector(row_id))
  
  write_csv(tab_data, path(output_root, "car-tables-figs/tbl-csv/tbl_5-2_sector_summary.csv"))
  
  res_gt <-
    tab_data %>%
    table_basic(rowname = "row_id") %>%
    tab_spanner(label = "Historical ", columns = all_of(show_years_hist_chr)) %>%
    tab_spanner(label = "Projected", columns = all_of(show_years_proj_chr)) %>%
    
    tab_stubhead(label = "Sector") %>%
    cols_hide(c(category, region, gas, unit)) %>%
    
    fmt_number(columns = all_of(show_years_chr), decimals = 0) %>%
    format_fake_summary_rows()
}

em_table_5_2 <- make_table_sector_summary()
table_output_wrapper(em_table_5_2, path(output_root, "car-tables-figs/tbl-png/tbl_5-2_sector_summary.png"))
```



### Table 5-3. Comparison of Total Gross GHG Emissions under the 2021 Policy Baseline Projections to Previous U.S. National Communications and Biennial Reports


```{r, opts.label = "rtf_out"}

gross_comp_table <- local({
  
  show_years <- c(2005, 2010, 2015, config$base_year, 2025, 2030, 2035)
  
  addl_data_old_car_gross <- read_csv(here("data-raw/additional-tables/t58_2020.csv"), col_types = cols())

  y2021_gross <- usproj_2021 %>%
    filter(category == "GrossTotal", gas == "Total", scenario %in% c("historical", "WM")) %>%
    mutate(Projection = "2021 NC") %>%
    select(Projection, year, value) %>%
    mutate(value = round(value, 1)) %>% # show 1 more decimal in change tracking than pub table
    pivot_wider(names_from = year, values_from = value)
  
  current_gross <- input_dataframe %>%
    filter(category == "GrossTotal", gas == "Total", scenario %in% c("historical", "WM")) %>%
    mutate(Projection = "2022 NC") %>%
    select(Projection, year, value) %>%
    mutate(value = round(value, 1)) %>% # show 1 more decimal in change tracking than pub table
    pivot_wider(names_from = year, values_from = value)
  
  gross_comp_data <- bind_rows(
    current_gross,
    y2021_gross,
    addl_data_old_car_gross
  ) %>%
    select(Projection, all_of(as.character(show_years)))
  
  write_csv(gross_comp_data, path(output_root, "car-tables-figs/tbl-csv/tbl_5-3_gross_comp.csv"))

  gross_comp_table <-
    gross_comp_data %>%
    table_basic(rowname = "Projection") %>%
    fmt_number(columns = any_of(as.character(show_years)), decimals = 0) 
})

table_output_wrapper(gross_comp_table, path(output_root, "car-tables-figs/tbl-png/tbl_5-3_gross_comp.png"))
```


### Table 5-5. Summary of Key Variables and Assumptions Used in the Projections Analysis

```{r, opts.label = "rtf_out"}

show_years <- c(2005, 2010, 2015, 2020, 2025, 2030, 2035)
show_years_chr <- as.character(show_years)
show_years_hist_chr <- as.character(show_years[show_years <= 2020])
show_years_proj_chr <- as.character(show_years[show_years > 2020])

br_key_variables_formatted_wide <-
  br_key_variables_formatted %>%
  select(-c(scenario)) %>%
  rename("Factor" = "variable") %>%
  mutate(unit = gsub("billion miles", "Billion miles", unit)) %>%
  mutate(unit = gsub("billion vehicle mile", "Billion miles", unit)) %>%
  mutate(unit = gsub("Btu quadrillion", "quads", unit)) %>%
  mutate(unit = gsub("quads", "Quads", unit)) %>%
  mutate(unit = gsub("million metric tons CO2", "MMTCO2e", unit)) %>%
  mutate(unit = gsub("million metric tons CO2", "MMTCO2e", unit)) %>%
  mutate(unit = gsub("Million people", "millions", unit)) %>%
  mutate(unit = gsub("thousand Btu/\\$ GDP", "Thousand Btu per Chained (2012) Dollar", unit)) %>%
  mutate(unit = gsub("billion 2012  \\$", "Billion chained (2012) dollars", unit)) %>%
  mutate(value = round(value, 2)) %>% # show 1 more decimal in change tracking than pub table
  pivot_wider(names_from = year, values_from = value)

t55_data <- br_key_variables_formatted_wide %>%
  select(Factor, unit, any_of(show_years_chr))

t55 <- t55_data %>%
  table_basic(rowname = "Factors") %>%
  cols_label(Factor = "Key Factor", unit = "Units") %>%
  fmt_number(columns = any_of(show_years_chr), decimals = 1) %>%
  tab_spanner(label = "Historical", columns = any_of(show_years_hist_chr)) %>%
  tab_spanner(label = "Projected", columns = any_of(show_years_proj_chr))

write_csv(br_key_variables_formatted_wide, path(output_root, "data-annex/drivers_data.csv"))
write_csv(t55_data, path(output_root, "car-tables-figs/tbl-csv/tbl_5-5_key_drivers.csv"))
table_output_wrapper(t55, path(output_root, "car-tables-figs/tbl-png/tbl_5-5_key_drivers.png"))

```


### Table 5-6. Comparison of Key Factors to Previous Climate Action Reports and Biennial Reports

```{r, opts.label = "rtf_out"}

t56 <- tar_read(t56)

t56_table_data <- 
  t56 %>%
  separate("Assumptions for 2030", c("Assumptions for 2030", "Units"), sep = "[\\(\\)]") %>% 
  mutate(Units = paste(toupper(substr(Units, 1, 1)), substr(Units, 2, nchar(Units)), sep="")) %>%
  mutate(across(.cols = 3:6, .fns = ~round(.x, 3))) # show 1 more decimal in change tracking than pub table
  
t56_table <- t56_table_data %>%
  rename(Variable = `Assumptions for 2030`) %>%
  table_basic(rowname = "Variable") %>%
  tab_stubhead(label = "Key Factor") %>% 
  tab_spanner(label = "Assumptions for 2030", columns = 3:6) %>%
  fmt_number(columns = 3:6, decimals = 2) %>%
  tab_footnote("Note: All dollar values are expressed in 2021 constant dollars, and were converted from original values using a GDP chain-weighted price index.")

write_csv(t56_table_data, path(output_root, "car-tables-figs/tbl-csv/tbl_5-6_drivers_comparison.csv"))
table_output_wrapper(t56_table, path(output_root, "car-tables-figs/tbl-png/tbl_5-6_drivers_comparison.png"))
```
Note: All dollar values converted to 2021 dollars.

## Table 5-7. Trends in Emissions from International Bunker Fuels

```{r, tabbunkers, opts.label = "rtf_out"}

make_bunkers_table <- function() {
  show_years <- c(2005, 2010, 2015, config$base_year, 2025, 2030, 2035)
  
  show_years_chr <- as.character(show_years)
  show_years_hist_chr <- as.character(show_years[show_years <= config$base_year])
  show_years_proj_chr <- as.character(show_years[show_years > config$base_year])
  
  bunkers <- usproj_emissions %>%
    filter(category == "Bunkers",
           scenario %in% c("historical", "WM"),
           region == "USA")
  
  stopifnot(! "Total" %in% unique(bunkers$gas)) # if so, then use Total instead of approach below
  stopifnot(unique(bunkers$unit) == "MMTCO2e")
  
  bunkers_summary <- bunkers %>%
    group_by(category, region, year, unit, scenario) %>%
    summarize(
      gas = "Total",
      value = sum(value, na.rm = TRUE),
      .groups = "drop"
    )
  
  tab_data <- bunkers_summary %>%
    filter(year %in% show_years) %>%
    select(-scenario) %>%
    mutate(value = round(value, 1)) %>% # show 1 more decimal in change tracking than pub table
    pivot_wider(names_from = year, values_from = value)
  
  write_csv(tab_data, path(output_root, "car-tables-figs/tbl-csv/tbl_bunkers.csv"))
  
  res_gt <-
    tab_data %>%
    mutate(category = "International Bunker Fuels") %>%
    table_basic(rowname = "category") %>%
    tab_spanner(label = "Historical ", columns = all_of(show_years_hist_chr)) %>%
    tab_spanner(label = "Projected", columns = all_of(show_years_proj_chr)) %>%
    
    #tab_stubhead(label = "Sector") %>%
    cols_hide(c(category, region, gas, unit)) %>%
    
    fmt_number(columns = all_of(show_years_chr), decimals = 0) %>%
    format_fake_summary_rows()
    
  res_gt
}

bunker_tbl <- make_bunkers_table()
table_output_wrapper(bunker_tbl, path(output_root, "car-tables-figs/tbl-png/tbl_bunkers.png"))
  

```



## Figures {.tabset}

### Figure 5-1. US Net Emissions Comparison

```{r, fig51, opts.label = "img_out", dev="svglite"}

tar_load(c(br2016_em_total, car2014_em_total, ghgi_em_total))

old_2005_base <- br2016_em_total$value[br2016_em_total$year == 2005]

new_2005_base <- ghgi_em_total$value[ghgi_em_total$year == 2005]
new_targets <- expand_grid(
    scenario = c("17% below 2005", "26% below 2005", "28% below 2005", "50% below 2005", "52% below 2005"),
    year = 2005:2035) %>%
  mutate(value = case_when(
    scenario == "17% below 2005" ~ new_2005_base * (1 - 0.17),
    scenario == "26% below 2005" ~ new_2005_base * (1 - 0.26),
    scenario == "28% below 2005" ~ new_2005_base * (1 - 0.28),
    scenario == "50% below 2005" ~ new_2005_base * (1 - 0.50),
    scenario == "52% below 2005" ~ new_2005_base * (1 - 0.52),
    TRUE ~ NA_real_)) %>%
  mutate(scn_grp = "new_targets")

perc_from_2005 <- function(em) {(em / new_2005_base) - 1}

usproj_2021_total <-
  usproj_2021 %>%
  filter(region == "USA") %>%
  filter(year <= 2035) %>%
  filter(
    is_source_total_cat(category, category_list), 
    !is_memo_item(category, category_list)
  ) %>%
  mutate(scenario = case_when(scenario %in% c("WM", "historical") ~ "2020 Policy (Baseline)",
                              scenario %in% c("WM-highseq") ~ "2020 Policy (High Sequestration)",
                              scenario %in% c("WM-lowseq") ~ "2020 Policy (Low Sequestration)")) %>%
  summarize_emissions_total()

usproj_emissions_total <-
  input_dataframe %>%
  filter(region == "USA") %>%
  filter(year <= 2035) %>%
  filter(
    is_source_total_cat(category, category_list), 
    !is_memo_item(category, category_list)
  ) %>%
  mutate(scenario = case_when(scenario %in% c("WM", "historical") ~ "2021 Policy (Baseline)",
                              scenario %in% c("WM-highseq") ~ "2021 Policy (High Sequestration)",
                              scenario %in% c("WM-lowseq") ~ "2021 Policy (Low Sequestration)")) %>%
  summarize_emissions_total()

compare_total <- 
  bind_rows(
    br2016_em_total,
    car2014_em_total,
    usproj_2021_total,
    ghgi_em_total,
    usproj_emissions_total,
  ) %>%
  mutate(scn_grp = case_when(str_detect(scenario, "^BR2016_WM") ~ "BR2016-WM",
                             str_detect(scenario, "^CAR2014_WM") ~ "NC2014-WM",
                             str_detect(scenario, "^2020 Policy") ~ "NC2021-WM",
                             str_detect(scenario, "^2021 Policy") ~ "NC2022-WM",
                             str_detect(scenario, "^GHGI2015") ~ "BR2016-WM",
                             str_detect(scenario, "^GHGI2022") ~ "NC2022-WM",
                             TRUE ~ scenario)) %>%
  filter(year >= 2000, year <= 2035)

base <-
  ggplot(data = compare_total, aes(x = year, y = value, color = scn_grp, group = scenario)) +
  geom_envelope(aes(group = scn_grp, fill = scn_grp), show.legend = FALSE, alpha = 0.2) +
  geom_line(linetype = "solid",
            size = 0.6,
            lineend = "round") +
  geom_point(data = filter(
    compare_total,
    (scenario == "GHGI2022" & year %in% c(2005, 2020))),
    size = 2) +
  scale_x_continuous(
    breaks = c(2005, 2010, 2015, 2020, 2025, 2030, 2035)
  ) +
  scale_y_continuous(
    breaks = seq(0, 7000, by = 1000),
    labels = scales::label_comma(accuracy = 1),
    sec.axis = sec_axis(
      name = "Percent below 2005",
      trans = perc_from_2005,
      breaks = seq(0, -.5, by=-0.05),
      labels = scales::label_percent(accuracy = 1)
    )
  ) + 
  scale_color_manual(
    aesthetics = c("colour", "fill"),
    limits = c("NC2022-WM", "NC2021-WM", "BR2016-WM", "NC2014-WM"),
    labels = c(
      "NC2022-WM" = "2021 Policy (2022 NC)",
      "NC2021-WM" = "2020 Policy",
      "BR2016-WM" = "2016 BR",
      "NC2014-WM" = "2014 CAR",
      "NC2010-WM" = "2010 CAR",
      "NC2006-WM" = "2006 CAR",
      "new_targets" = "new_targets"
    ),
    values = c(
      "NC2022-WM" = "steelblue",
      "NC2021-WM" = "darkgreen",
      "BR2016-WM" = "sienna",
      "NC2014-WM" = "grey62",
      "NC2010-WM" = "mediumpurple",
      "NC2006-WM" = "coral4",
      "new_targets" = "grey15"
    )
  ) +
  geom_vline(aes(xintercept = config$base_year), alpha = 0.5, linetype = "dotted") +
  geom_hline(aes(yintercept = new_2005_base), alpha = 0.5, linetype = "dotted") +

  geom_line(data = new_targets, linetype = "dashed") +
  geom_point(data = filter(
    new_targets, 
    (scenario == "17% below 2005" & year %in% c(2005, 2020)) |
      (scenario == "26% below 2005" & year %in% c(2005, 2025)) |
      (scenario == "28% below 2005" & year %in% c(2005, 2025)) | 
      (scenario == "50% below 2005" & year %in% c(2005, 2030)) |
      (scenario == "52% below 2005" & year %in% c(2005, 2030))),
    size = 2) +
  geom_label(data = filter(new_targets, year == 2005), aes(x = min(year), label = scenario), 
             nudge_x = -3.5, size = 3.4, show.legend = FALSE) + 
  coord_cartesian(
    xlim = c(2000, 2035),
    ylim = c(3000, NA)
  ) +
  labs(
    x = "Year", 
    y = expression("MMT"~CO[2]*"e")) +
  theme_car_proj(base_size = 10)

compare_total_fig <- base

write_csv(compare_total, path(output_root, "car-tables-figs/fig-data/fig_5-1_compare_net_total.csv"))
ggsave(path(output_root, "car-tables-figs/fig-svg/fig_5-1_compare_net_total.svg"), plot = compare_total_fig)
#knitr::include_graphics(path(output_root, "car-tables-figs/fig-svg/fig_5-1_compare_net_total.svg"))
compare_total_fig
```


### Figure 5-2. Comparison of Climate Action Report Baseline “With Measures” Projections of Gross Greenhouse Gas Emissions

```{r, fig52, opts.label = "img_out", dev="svglite"}

addl_data_old_car_gross <- read_csv(here("data-raw/additional-tables/t58_2020.csv"), col_types = cols()) %>%
  select(-GWP)

t58_long <- addl_data_old_car_gross %>%
  pivot_longer(
    cols = -Projection,
    names_to = "year", 
    values_to = "value") %>%
  filter(!is.na(value)) %>%
  mutate(year = as.numeric(year))

usproj_2021_gross <- usproj_2021 %>%
  filter(category == "GrossTotal", gas == "Total", scenario %in% c("historical", "WM")) %>%
  mutate(Projection = "2020 Policy") %>%
  select(Projection, year, value)

current_gross <- input_dataframe %>%
  filter(category == "GrossTotal", gas == "Total", scenario %in% c("historical", "WM")) %>%
  mutate(Projection = "2021 Policy") %>%
  select(Projection, year, value)

f52 <- bind_rows(
  t58_long,
  usproj_2021_gross,
  current_gross
) %>% arrange(desc(Projection), desc(year))
  
fig_gross_comp <- f52 %>%
  better_lineplot("year", "value", groupcol = "Projection") + 
  scale_y_continuous(
    labels = scales::label_comma(),
    breaks = c(2000, 3000, 4000, 5000, 6000, 7000, 8000, 9000, 10000), 
    limits = c(2900, 9100)
  ) +
  scale_color_manual(
    aesthetics = c("colour", "fill"),
    limits = c("2006 NC", "2010 NC", "2014 NC", "2016 BR", "2020 Policy", "2021 Policy"),
    values = c(
      "2021 Policy" = "steelblue",
      "2020 Policy" = "darkgreen",
      "2016 BR" = "sienna",
      "2014 NC" = "grey62",
      "2010 NC" = "mediumpurple",
      "2006 NC" = "coral4",
      "new_targets" = "grey15"
    )) +
  lims(x = c(1990, 2035)) +
  labs(
    x = "Year",
    y = expression("MMT"~CO[2]*"e")
  ) +
  theme_car_proj() +
  theme(legend.position = c(0.2, 0.35))

write_csv(f52, path(output_root, "car-tables-figs/fig-data/fig_5-2_compare_gross_total.csv"))
ggsave(path(output_root, "car-tables-figs/fig-svg/fig_5-2_compare_gross_total.svg"), plot = fig_gross_comp)
#knitr::include_graphics(path(output_root, "car-tables-figs/fig-svg/fig_5-2_compare_gross_total.svg"))
fig_gross_comp
```

### Figure 5-3. AEO Comparison

```{r, fig53, opts.label = "img_out"}

aeo_evo_total <- aeo_evo_data %>%
  filter(variable == "CO2 emissions", econ_sector == "total")
  
fig_aeo_comp <- 
  aeo_evo_total %>% 
  better_lineplot("year", "value", "publication") +
  scale_y_continuous(breaks = c(3000, 4000, 5000, 6000, 7000, 8000, 9000), limits = c(3900, 7100)) +
  labs(
    x = "Year",
    y = expression("MMT"~CO[2]*"e")
  ) +
  theme_car_proj()

write_csv(aeo_evo_total, path(output_root, "car-tables-figs/fig-data/fig_5-3_aeo_comparison.csv"))
ggsave(path(output_root, "car-tables-figs/fig-svg/fig_5-3_aeo_comparison.svg"), plot = fig_aeo_comp)
#knitr::include_graphics(path(output_root, "car-tables-figs/fig-svg/fig_5-3_aeo_comparison.svg"))
fig_aeo_comp
```

### Figure 5-4. Normalized Kaya Identity Factors Used for Assessing the Effects of New Policies and Measures

```{r, fig54, opts.label = "img_out"}
 
normyear <- 2012

tar_load(c(kaya_decomp_ratios_alt, kaya_decomp_factors_alt))

kaya_decomp_ratios_normed <- kaya_decomp_ratios_alt %>%
  group_by(Projection, variable) %>%
  mutate(value_normed = value / value[year==normyear])

fig_kaya_factors <- kaya_decomp_ratios_normed %>%
  filter(year %in% 2010:2030) %>%
  ggplot(aes(x = year, y = value_normed, color = variable, linetype = Projection)) +
  scale_linetype_manual(values = c("dashed", "solid"))+
  geom_line(size = 0.6, alpha = 0.8, lineend="round") +
  scale_y_continuous(limits = c(0.25, 1.75)) +
  geom_vline(aes(xintercept = normyear), alpha = 0.3, linetype = "dotted") +
  labs(
    x = "Year",
    y = "Kaya Factor Index\n(2012=1.0)"
  ) + 
  theme_car_proj()

write_csv(kaya_decomp_ratios_normed, path(output_root, "car-tables-figs/fig-data/fig_5-4_kaya_factors.csv"))
ggsave(path(output_root, "car-tables-figs/fig-svg/fig_5-4_kaya_factors.svg"), plot = fig_kaya_factors)
#knitr::include_graphics(path(output_root, "car-tables-figs/fig-svg/fig_5-4_kaya_factors.svg"))
fig_kaya_factors
```





