---
pagetitle: "2024 Biennial Transparency Report Projections Chapter: Historical and Projected GHG Tables & Figures"
output:
  html_document:
    number_sections: false
    highlight: tango
    fontsize: 12
    fig_caption: false
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
params:
  mode: "interactive"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", fig.width = 9, fig.height = 7)
```

```{r}
source('packages.R')
library(targets)
library(tarchetypes)
tar_source()
```

```{r}

tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm,
    total_gross_emissions,
    ghgi_comp_tab,
    figmap_nrgco2_stackbar,
    past_proj
    )
  )

# Drop USREP-ReEDS results for 2045 and 2050
projections_all_sm <- projections_all_sm %>%
  filter(!(grepl("usrr", proj_name) & year %in% c('2045','2050')))

total_gross_emissions <- total_gross_emissions %>%
  filter(!(grepl("usrr", proj_name) & year %in% c('2045','2050')))

source("scripts/theming.R")

```

# BTR Tables and Figures

## Value Summary Tables {.tabset}

### Gas

```{r gas summary}
gas_df <- create_summary_table50('gas','wm', projections_all_sm, config, settings)

gas_table <- create_html_table50(gas_df, 'Gas', settings)

gas_table_merged <- create_html_table_merged50(gas_df, 'Gas', settings)
gas_table_merged
```

```{r}
dir.create(paste0('output/',settings$version,"/tables_figs/to2050/results_tables/"))
dir.create(paste0('output/',settings$version,"/tables_figs/to2050/results_tables/by_gas_sector/"))

filename <- paste0("gas_table_",Sys.Date(),".png")
gtsave(gas_table_merged, paste0('output/',settings$version,"/tables_figs/results_tables/to2050/by_gas_sector/",filename))
```

### Sector

```{r sector summary}
sector_df <- create_summary_table50('usproj_sector', 'wm', projections_all_sm, config, settings)

sector_table <- create_html_table50(sector_df, 'Sector', settings)

sector_table_merged <- create_html_table_merged50(sector_df, 'Sector', settings)
sector_table_merged
```

```{r}

filename <- paste0("sector_table_",Sys.Date(),".png")
gtsave(sector_table_merged, paste0('output/',settings$version,"/tables_figs/to2050/results_tables/by_gas_sector/",filename))
```

## 2005 Percent Change Table {.tabset}

### Gas

```{r, pct change by gas}
# TODO: @morgan update these % reduction tables to look like the gas and sector tables - i want historical trends in there and for the ranges to be presented with "-"
pct_change_table_gas <- create_pct_change_table50('gas', 'wm', projections_all_sm, config, settings)
pct_change_html_gas <- create_pct_change_html_table50(pct_change_table_gas, 'Gas', settings)
pct_change_html_gas
```

```{r}
dir.create(paste0('output/',settings$version,"/tables_figs/to2050/results_tables/percent_change_2005/"))
filename <- paste0("gas_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_gas, paste0('output/',settings$version,"/tables_figs/to2050/results_tables/percent_change_2005/",filename))
```

### Sector

```{r, pct change by sector}
pct_change_table_sector <- create_pct_change_table50('usproj_sector', 'wm', projections_all_sm, config, settings)
pct_change_html_sector <- create_pct_change_html_table50(pct_change_table_sector, 'Sector', settings)
pct_change_html_sector
```

```{r}
filename <- paste0("sector_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_sector, paste0('output/',settings$version,"/tables_figs/to2050/results_tables/percent_change_2005/",filename))
```

## BTR Main Plot {.tabset}

```{r}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum)) %>%
  filter(year %in% config$fives50)

ghgi = net_ghg %>% 
  filter(proj_name == "ghgi") %>% 
  mutate(grouping = "Historical")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == settings$base_year,]$sum
baseline = ghgi[ghgi$year == 2005,]$sum

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = settings$base_year,
    sum = ghgi$sum[ghgi$year == settings$base_year])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year)) %>%
  filter(grouping %in% c('wm')) %>%
  mutate(grouping = case_when(
    grouping == "wm"~"2024 Policy Baseline",
    grouping == "IRA" ~ "LEEP",
    TRUE~grouping))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c((baseline * (1-.169)), (baseline * (1-.26)), (baseline * (1-.50))),
  ymax = c((baseline * (1-.171)), (baseline * (1-.28)), (baseline * (1-.52))),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Net GHG Emissions

```{r}
projections = br_project50(ghgi, proj, settings, targets = ndc_targets)
projections
```

```{r}
filename <- paste0("btr_main_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/btr_main_figs/main_fig/",filename), create.dir = TRUE, height = 5.5)
```

```{r}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum),.groups = 'drop') %>%
  filter(year %in% config$fives50) %>%
  mutate(pct_change_05 = round((sum/sum[year==2005]-1),2))

ghgi = net_ghg %>% 
  filter(proj_name == "ghgi") %>%
  mutate(grouping = "Historical")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == settings$base_year,]$pct_change_05
baseline = ghgi[ghgi$year == 2005,]$pct_change_05

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = settings$base_year,
    pct_change_05 = ghgi$pct_change_05[ghgi$year == settings$base_year])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year)) %>%
  filter(grouping == 'wm') %>%
  mutate(grouping = "2024 Policy Baseline")

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c(-.17, -.28, -.52),
  ymax = c(-.17, -.26, -.5),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Percent Change from 2005

```{r}
projections_pct_change = br_project_pct_change50(ghgi, proj, targets = ndc_targets)
projections_pct_change
```

```{r}
filename <- paste0("btr_main_fig_pctchange05_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/btr_main_figs/pct_change/",filename), create.dir = TRUE, height = 6)
```

## BTR Main Plot w/ LEEP Report Comparison {.tabset}

```{r data}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum)) %>%
  filter(year %in% config$fives50)

ghgi = net_ghg %>% 
  filter(proj_name == "ghgi") %>% 
  mutate(grouping = "Historical")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == settings$base_year,]$sum
baseline = ghgi[ghgi$year == 2005,]$sum

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = settings$base_year,
    sum = ghgi$sum[ghgi$year == settings$base_year])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year)) %>%
  filter(grouping %in% c("IRA", 'wm')) %>%
  mutate(grouping = case_when(
    grouping == "wm"~"2024 Policy Baseline",
    grouping == "IRA" ~ "LEEP",
    TRUE~grouping))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c((baseline * (1-.169)), (baseline * (1-.26)), (baseline * (1-.50))),
  ymax = c((baseline * (1-.171)), (baseline * (1-.28)), (baseline * (1-.52))),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Net GHG Emissions

```{r proj function}
projections_leep = br_project50(ghgi, proj, settings, targets = ndc_targets)
projections_leep
```

```{r}
filename <- paste0("btr_main_fig_leep_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/btr_main_figs/main_fig_leep/",filename), create.dir = TRUE, height = 6)
```

```{r}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum),.groups = 'drop') %>%
  filter(year %in% config$fives50) %>%
  mutate(pct_change_05 = round((sum/sum[year==2005]-1),2))

ghgi = net_ghg %>% 
  filter(proj_name == "ghgi") %>%
  mutate(grouping = "Historical")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == settings$base_year,]$pct_change_05
baseline = ghgi[ghgi$year == 2005,]$pct_change_05

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = settings$base_year,
    pct_change_05 = ghgi$pct_change_05[ghgi$year == settings$base_year])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year)) %>%
  filter(grouping %in% c("IRA",'wm')) %>%
  mutate(grouping = case_when(
    grouping == "wm"~"2024 Policy Baseline",
    grouping == "IRA" ~ "LEEP",
    TRUE~grouping))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c(-.17, -.28, -.52),
  ymax = c(-.17, -.26, -.5),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Percent Change from 2005

```{r}
projections_pct_change = br_project_pct_change50(ghgi, proj, targets = ndc_targets)
projections_pct_change
```

```{r}
filename <- paste0("btr_main_fig_pctchange05_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/btr_main_figs/main_fig_leep/",filename), create.dir = TRUE)
```

## BTR Net-GHG Stackbar

```{r, fig.width=15}
net_ghg_sb_df <- net_ghg_sb_data_processing(projections_all_sm, config, settings)
net_ghg_stackbar <- br_project_net_ghg_sb(net_ghg_sb_df, config)
net_ghg_stackbar
```

# Kaya Analysis

```{r}

dat = data_long_clean |> 
  filter(variable %in% c("Emissions|CO2|Energy", "Final Energy", "GDP|MER", "Population")) |>
  select(-unit) |> 
  spread(variable, value) |> 
  mutate(EmissPerEnergy = `Emissions|CO2|Energy`/`Final Energy`,
         EnergyPerGDP = `Final Energy`/`GDP|MER`,
         GDPPerCap = `GDP|MER`/`Population`) 

dat2 = dat |> 
  filter(year == 2020) |> 
  select(-`Emissions|CO2|Energy`, -`Final Energy`, -`GDP|MER`) |> 
  rename(EmissPerEnergyBase = EmissPerEnergy,
         EnergyPerGDPBase = EnergyPerGDP,
         GDPPerCapBase = GDPPerCap,
         PopulationBase = Population) |> 
  select(-year)

dat3 = dat |> 
  left_join(dat2) |> 
  select(-`Emissions|CO2|Energy`, -`Final Energy`, -`GDP|MER`) |> 
  mutate(EmissPerEnergyIn = EmissPerEnergy/EmissPerEnergyBase,
         EnergyPerGDPIn = EnergyPerGDP/EnergyPerGDPBase,
         GDPPerCapIn = GDPPerCap/GDPPerCapBase,
         PopulationIn = Population/PopulationBase) |> 
  filter(region == "United States") |> 
  select(model,scenario,year,datasrc,region,EmissPerEnergyIn,EnergyPerGDPIn,GDPPerCapIn,PopulationIn) |> 
  pivot_longer(cols = 6:9, names_to = "var", values_to = "value")

dat_range <- dat3 %>%
  filter(scenario == 'wm') %>%
  filter(var %in% c('EnergyPerGDPIn', 'EmissPerEnergyIn')) %>%
  filter(year %in% config$fives_proj) %>% 
  group_by(year, var) %>%
  summarise(ymax = max(value),
              ymin = min(value),
              med = median(value))

dat4 <- dat3 %>%
  filter(scenario == 'wm') %>%
  filter(!var %in% c('EnergyPerGDPIn', 'EmissPerEnergyIn')) %>%
  filter(year %in% config$fives_proj) %>%
  group_by(year, var) %>%
  summarise(med = median(value))

var_palette = c(unique(dat_range$var),unique(dat4$var))

```

```{r}

##### use real historic data 
##### use Each model's internal rate of change for energy
##### leave emissions as is for now and see how it looks


# TODO: we should use annual projections for br2024 for pop and gdp/capita, see if this makes a difference in smoothing out the gdp/cap trend

tar_load(kaya_comparison50) 

kaya_data_range = kaya_comparison50 %>% 
  filter(br_version == "2024") %>% 
  select(-value,-base) %>% 
  spread(scenario, indexed) %>%
  mutate(
    variable = case_when(
      variable == "EmissPerEnergy" ~ "Emissions/Energy",
      variable == "EnergyPerGDP" ~ "Energy/GDP",
      variable == "GDPPerCap" ~ "GDP/Capita",
      TRUE~variable),
    br_version = case_when(
      br_version == "2022" ~ "2022 BR",
      br_version == "2024" ~ "2024 BTR",
      TRUE ~ br_version)) %>%
  filter(year <= 2050 & year >=2005)

kaya_comp_renamed = kaya_comparison50  %>%
  mutate(
    variable = case_when(
      variable == "EmissPerEnergy" ~ "Emissions/Energy",
      variable == "EnergyPerGDP" ~ "Energy/GDP",
      variable == "GDPPerCap" ~ "GDP/Capita",
      TRUE~variable),
    br_version = case_when(
      br_version == "2022" ~ "2022 BR",
      br_version == "2024" ~ "2024 BTR",
      TRUE ~ br_version)) %>%
  filter(!(br_version == "2024 BTR" & variable %in% c("Emissions/Energy","Energy/GDP") & year >2022)) %>%
  filter(year <= 2050 & year >=2005)

var_palette = unique(kaya_data_range$variable)

multipanel_kaya = ggplot()+
  geom_line(data = kaya_comp_renamed,
            aes(x = year, y = indexed, color = variable)) +
  geom_ribbon(data = kaya_data_range, 
              aes(x=year, ymin = min, ymax = max, fill = variable))+
  xlim(2005,2050) + 
  ylim(0.5,1.6) + 
  facet_wrap(~br_version) +
  scale_subpalette_single(var_palette) +
  theme_btr() +
  labs(y="Key Factor Index \n(2015 = 1.0)")
multipanel_kaya
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/kaya/kaya_multipanel.png"), width = 5, create.dir = TRUE)

line_size = 0.7

singlepanel_kaya = ggplot()+
  geom_line(data = (kaya_comp_renamed %>% 
                      filter(br_version %in% c("2022 BR","2024 BTR")) %>%
                      filter(!(br_version == "2022 BR" & year >2035))),
            aes(x = year, y = indexed, color = variable, linetype = br_version),
            size = line_size) +
  geom_ribbon(data = kaya_data_range, 
              aes(x=year, ymin = min, ymax = max, fill = variable, color = variable),
              alpha = 0.4,
              outline.type = "both",
              size = line_size) +
  ylim(0.5,1.6) + 
  scale_subpalette_single(var_palette) +
  scale_linetype_manual(values = c("2022 BR" = "dotted", "2024 BTR" = "solid")) +
  theme_btr() +
  labs(y="Key Factor Index \n(2015 = 1.0)") +
  bottom1 +
  scale_x_continuous(breaks = config$table50,expand = c(0,0)) +
  geom_vline(xintercept = settings$base_year,
               linetype = 'dashed',
               color = "black",
              # size = 0.4,
               alpha = 0.5
              ) +
  theme(panel.grid.minor.x = element_blank()) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  theme(legend.background = element_rect(color = NA))
singlepanel_kaya
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/kaya/kaya_singlepanel.png"), width = 5, create.dir = TRUE)
```

```{r}
Kaya <- function(dat_range, dat4, var_palette){
  ggplot() +
    geom_line(dat4, mapping = aes(year,med, group = var, color = var),size = 0.7) +
    geom_ribbon(dat_range, mapping = aes(x = year,ymax = ymax, ymin = ymin,
                                                  fill = var, 
                                                  color = var),
                alpha = 0.4 ,
                size = 0.7) +
    scale_subpalette_single(var_palette) +
    labs(x = 'Year',
         y = 'Kaya Factor Index') +
    theme(
      legend.position = "inside",
      legend.position.inside = c(0.15, 0.2))
}

fig <- Kaya(dat_range, dat4, var_palette)
#fig
```

```{r}
filename <- paste0("kaya_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/kaya/",filename), create.dir = TRUE)
```

# Sector Analysis {.tabset}

```{r}
sector_vars = c("Emissions|CO2|Energy|Demand|Buildings|Total",
                         "Emissions|CO2|Energy|Demand|Transportation|Total",
                         "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
                         "Emissions|CO2|Energy|Supply|Electricity")
lts_vars = c("Emissions|CO2|Energy|Demand|Buildings|TotalDI",
                         "Emissions|CO2|Energy|Demand|Transportation|TotalDI",
                         "Emissions|CO2|Energy|Demand|Industry|TotalDI",
                         "Emissions|CO2|Energy|Supply|Electricity")

# ghgi 24 data
ghgi_df = ghgi_comp_tab %>%
  filter(model == config$model_hist) %>%
  filter(year %in% config$hist) %>%
  filter(variable %in% c(sector_vars,"Emissions|CO2|Energy|Demand|Industry|Total")) %>%
  mutate(variable = case_when(
    variable == "Emissions|CO2|Energy|Demand|Industry|Total" ~ "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
    TRUE~variable
  ))
# TODO: need to pull fuel production emissions from GHGI and create a new variable so that it can be included here for historical emissions

# LTS models and variables used for sector figures
lts_df = data_long_clean %>%
  filter(model %in% config$model_lts) %>%
  filter(year %in% config$fives50) %>%
  filter(variable %in% lts_vars) %>%
  # change names to match template update variable names
  mutate(variable = case_when(
    str_detect(variable, "Buildings") ~ "Emissions|CO2|Energy|Demand|Buildings|Total",
    str_detect(variable, "Transportation") ~ "Emissions|CO2|Energy|Demand|Transportation|Total",
    str_detect(variable, "Industry") ~ "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
    TRUE~variable))

# models used in the projections and variables used for sector figures
proj_models = config$model_wm
proj_df = data_long_clean %>%
  filter(model %in% proj_models) %>%
  filter(year %in% config$fives50) %>%
  filter(scenario == "wm") %>%
  filter(variable %in% sector_vars) %>%
  filter(region == 'United States')

# 2030 and 2035 projections medians
median_df = proj_df %>%
  group_by(year,variable) %>%
  summarise(value = median(value)) %>%
  mutate(model = "median",
         scenario = "wm",
         unit = "Mt CO2/yr",
         datasrc = "median calc",
         region = "United States") %>%
  select(names(proj_df))

# merge three datasets together
sector_df = rbind(ghgi_df, lts_df, proj_df, median_df) %>%
  mutate(type = case_when(
    str_detect(model, "LTS") ~ "LTS",
    model %in% proj_models ~ "proj",
    model == "EPA-GHGI" ~ "GHGI",
    model == "median" ~ "median",
    TRUE~model)) 
```

```{r}
# buildings
buildings = br_sectors50(sector_df,
                       "Emissions|CO2|Energy|Demand|Buildings|Total",
                       expression(paste("Buildings Emissions (MMt C", O[2], ")")))

# electricity
electricity = br_sectors50(sector_df,
                       "Emissions|CO2|Energy|Supply|Electricity",
                       expression(paste("Electricity Emissions (MMt C", O[2], ")")))

# transportation
transportation = br_sectors50(sector_df,
                       "Emissions|CO2|Energy|Demand|Transportation|Total",
                       expression(paste("Transportation Emissions (MMt C", O[2], ")")))

# industry
industry = br_sectors50(sector_df,
                       "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
                       expression(paste("Industry Emissions (MMt C", O[2], ")")))
```

## Buildings

```{r}
buildings
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/sector_analysis/buildings_comparison.png"), create.dir = TRUE, height = 4.5)
```

## Electricity

```{r}
electricity
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/sector_analysis/electricity_comparison.png"), create.dir = TRUE, height = 4.5)
```

## Transportation

```{r}
transportation
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/sector_analysis/transportation_comparison.png"), height = 4.5)
```

## Industry

```{r}
industry
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/sector_analysis/industry_comparison.png"), create.dir = TRUE, height = 4.5)
```

```{r}
# Stats for Emissions Projections and Trends by Sector DRAFT SECTION

# Energy
nrg_ch4 <- projections_all_sm %>% filter(grouping == 'wm',gas == 'CH4',usproj_sector == 'Energy',year %in% config$table) %>% select(year, sum, pct_change_05) %>% distinct()

nrg_co2 <- projections_all_sm %>% filter(grouping == 'wm',gas == 'CH4',usproj_sector == 'Energy',year %in% config$table) %>% select(year, sum, pct_change_05) %>% distinct()

# Electricity
gen_subset_sector_df <- function(sector_df, var_choice) {
  sector_df %>%
    filter(variable == var_choice,
           region == 'United States',
           scenario %in% c('Historic','wm'),
           year %in% config$table) %>%
    select(year,value) %>% 
    mutate(pct_change_05 = round((value/value[year==2005]-1),2)) %>%
    distinct()
}
  
elec_df = gen_subset_sector_df(sector_df, "Emissions|CO2|Energy|Supply|Electricity")

industry_df <- gen_subset_sector_df(sector_df, "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total")

trn_df <- gen_subset_sector_df(sector_df, "Emissions|CO2|Energy|Demand|Transportation|Total")

buildings_df <- gen_subset_sector_df(sector_df, "Emissions|CO2|Energy|Demand|Buildings|Total")

# View(elec_df)
# View(industry_df)
# View(trn_df)
# View(buildings_df)

```

# Past Report Comparison

## Total Gross Emissions {.tabset}

```{r}
# Load in past NCBR data
past_proj_clean <- past_proj %>%
  select(Report, Year, Emissions) %>%
  rename(Value = Emissions) %>%
  filter(Year <= 2035)

past_proj_clean_hilow <- past_proj_clean %>%
  group_by(Report,Year) %>%
  mutate(low = min(Value),
         high = max (Value),
         Report = case_when(Report == "btr_2024" ~ "2024 BTR",
                            Report == "car_2014" ~ "2014 CAR",
                            Report == "br_2016" ~ "2016 BR",
                            Report == "br_2021" ~ "2021 BR",
                            Report == "br_2022" ~ "2022 BR")) %>%
  select(Report,Year,low,high)
```

```{r}
col_order <- c('category', 'year', 'low', 'high')
category = 'gas'
group = 'wm'

summary <- projections_all_sm %>%
  rename(category = .data[[category]]) %>%
  filter(grouping %in% c(group,'ghgi')) %>%
  filter(year %in% config$seq_ncbr_comp_sm50) %>%
  group_by(proj_name, category, year) %>%
  summarise(cat_sum = sum(sum), .groups = 'drop')

summary_total_gross <- summary %>%
  filter(!category == 'LULUCF Sink') %>%
  group_by(proj_name, year) %>%
  summarise(value = sum(cat_sum), .groups = 'drop') %>%
  group_by(year) %>%
  mutate(low = min(value), high = max(value)) %>%
  select(year, low, high) %>%
  distinct() %>%
  mutate(category = 'Total Gross Emissions') %>%
  select(all_of(col_order)) %>%
  rename(Projection = category) %>%
  mutate(Projection = '2024 BTR')

tge_all_long_high_low <- summary_total_gross %>%
  rename(Report = Projection,
         Year = year) %>%
  rbind(past_proj_clean_hilow) %>%
  filter(Year %in% config$seq_ncbr_comp_sm50) %>%
  drop_na() %>%
  rename(Publication = Report)

proj_years <- c('2025', '2030', '2035', '2040','2045','2050')
hist_years <- c('2005', '2010', '2015', '2020')
proj_col_order <- c(
  '2025_low',
                      '2025_high',
                      '2030_low',
                      '2030_high',
                      '2035_low',
                      '2035_high',
                      '2040_low',
                      '2040_high',
                      '2045_low',
                      '2045_high',
                      '2050_low',
                      '2050_high'
)

df_low <- tge_all_long_high_low %>%
  select(Publication, Year, low) %>%
  pivot_wider(names_from = 'Year', values_from = 'low')


df_high <- tge_all_long_high_low %>%
  select(Publication, Year, high) %>%
  pivot_wider(names_from = 'Year', values_from = 'high')

df_merged <- merge(df_low[, c('Publication', proj_years)],
                   df_high[, c('Publication', proj_years)],
                   by = 'Publication',
                   suffix = c('', '_high'))

for (year in proj_years) {
  colnames(df_merged)[colnames(df_merged) == year] <- paste0(year, '_low')
  colnames(df_merged)[colnames(df_merged) == paste0(year, '_high')] <- paste0(year, '_high')
}

df_merge_final <- merge(df_low %>% select(Publication, all_of(hist_years)), df_merged) %>%
  select(Publication, all_of(hist_years), all_of(proj_col_order)) %>%
  mutate_if(is.numeric, round)

numeric_cols <- sapply(df_merge_final, is.numeric)
df_merge_final[, numeric_cols] <- lapply(df_merge_final[, numeric_cols], scales::comma)

ncbr_table_df <- df_merge_final
for (col in names(ncbr_table_df)) {
  ncbr_table_df <- ncbr_table_df %>%
    mutate(col = as.character(col)) %>%
    select(names(df_merge_final)) %>%
    arrange(desc(Publication))
}
```

### Table

```{r}
proj_col_order <- c('2025', '2030', '2035', '2040')
stubhead <- 'Publication'

merged = ncbr_table_df %>%
    mutate(
      `2025` = case_when(
        `2025_low` == `2025_high` ~ `2025_high`,
        `2025_low` != `2025_high` ~ paste0(`2025_low`," - ",`2025_high`)),
      `2030` = case_when(
        `2030_low` == `2030_high` ~ `2030_high`,
        `2030_low` != `2030_high` ~ paste0(`2030_low`," - ",`2030_high`)),
      `2035` = case_when(
        `2035_low` == `2035_high` ~ `2035_high`,
        `2035_low` != `2035_high` ~ paste0(`2035_low`," - ",`2035_high`)),
      `2040` = case_when(
        `2040_low` == `2040_high` ~ `2040_high`,
        `2040_low` != `2040_high` ~ paste0(`2040_low`," - ",`2040_high`)),
      `2045` = case_when(
        `2045_low` == `2045_high` ~ `2045_high`,
        `2045_low` != `2045_high` ~ paste0(`2045_low`," - ",`2045_high`)),
      `2050` = case_when(
        `2050_low` == `2050_high` ~ `2050_high`,
        `2050_low` != `2050_high` ~ paste0(`2050_low`," - ",`2050_high`))
    ) %>%
    select(-contains("_"))

bold1 = nrow(merged) - 3
bold2 = nrow(merged) - 1
bold3 = nrow(merged) - 5

ncbr_comp_table <- merged %>%
  
  gt() %>%
  cols_align('center', columns = everything()) %>%
  cols_align('left', columns = stubhead) %>%
  # tab_style(
  #   style = cell_borders(
  #     color = "#1F77AE",
  #     sides = c("bottom"),
  #     weight = px(2)
  #   ),
  #   #
  #   locations = cells_body(rows = c(bold1, bold2, bold3))
  # ) %>% 

  
  gt_theme_nc_blue()

ncbr_comp_table
```

```{r}
dir.create(paste0('output/',settings$version,"/tables_figs/to2050/results_tables/ncbr_comparison/"))

filename <- paste0("ncbr_comp_table_",Sys.Date(),".png")
gtsave(ncbr_comp_table, paste0('output/',settings$version,"/tables_figs/to2050/results_tables/ncbr_comparison/",filename))
```


```{r}
tge_btr <- projections_all_sm %>% 
  filter(!gas == 'LULUCF Sink') %>%
  group_by(proj_name, grouping, year) %>%
  summarise(Value = sum(sum),.groups = 'drop')

tge_all_long <- tge_btr %>%
  mutate(Report = 'btr_2024') %>%
  rename(Year = year) %>% 
  select(names(past_proj_clean)) %>%
  rbind(past_proj_clean) %>%
  mutate(Year = as.numeric(Year),
         Report = case_when(Report == "btr_2024" ~ "2024 BTR",
                            Report == "car_2014" ~ "2014 CAR",
                            Report == "br_2016" ~ "2016 BR",
                            Report == "br_2021" ~ "2021 BR",
                            Report == "br_2022" ~ "2022 BR"))
#%>%
 # filter(year %in% config$fives_proj_sm)


ncbr_comp_ribbon <- tge_all_long %>% 
  group_by(Report,Year) %>%
  mutate(min = min(Value),
         max = max(Value)) %>%
  select(Report,Year,min,max) %>%
  distinct()
```

### Figure

```{r}
fig <- ncbr_comparison_figure50(ncbr_comp_ribbon, tge_all_long, settings, config)
fig
```

```{r}
filename <- paste0("ncbr_comp_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/ncbr_comparison/",filename), create.dir = TRUE)
```


### Figure: From 1990

```{r}
fig <- ncbr_comp_fig_1990_50(ncbr_comp_ribbon, tge_all_long, settings, config)
fig

```

```{r}
filename <- paste0("ncbr_comp90_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/ncbr_comparison/",filename))
```

# Energy CO2 Emissions Range

```{r}

nrg_emissions <- projections_all_sm %>%
  filter(usproj_sector %in% c('Energy','Transportation') & gas == "CO2") %>%
  filter(grouping %in% c('ghgi','wm')) %>%
  group_by(proj_name, year, grouping) %>%
  summarise(nrg_trn_co2 = sum(sum)) %>%
  filter(year %in% config$annual_1990_fives50) 

ghgi <- nrg_emissions %>%
  filter(year <= settings$base_year)

proj <- nrg_emissions %>%
  group_by(year) %>% 
  filter(year >= settings$base_year)%>%
    summarise(ymax = max(nrg_trn_co2),
              ymin = min(nrg_trn_co2),
              med = median(nrg_trn_co2),
              .groups = 'drop')

nrg_color <- "#2EAD96"

fig <- 
  ggplot() +
  geom_line(ghgi, mapping = aes(x = year, y = nrg_trn_co2, color = proj_name), color = nrg_color, size = 0.7) +
  geom_ribbon(proj, mapping = aes(x = year,ymax = ymax, ymin = ymin),
              color = nrg_color,
              fill = nrg_color,
              alpha = 0.4 ,
              size = 0.7)+
    labs(x = 'Year',
         y = expression(paste("MMt ", CO[2], sep = ""))) +
    geom_vline(
      xintercept = 2022,
      linetype = 'dashed',
      color = "black",
      # size = 0.4,
      alpha = 0.5) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(breaks = c(seq(1990,2020,by=5), 2022, seq(2025,2050,by=5)), expand = c(0,0)) +
    theme_btr() 
  
fig
```

```{r}
filename <- paste0("nrg_emissions_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/to2050/nrg_emissions/",filename), create.dir = TRUE,height = 4.5)
```

# LULUCF Sink Range

```{r}

lulucf_co2_hist <- read_xlsx(
  "data-extra/USDA NFS Raw Data/LULUCF projections DRAFT compilation 82924.xlsx",
  sheet = "Table 6-2",
  skip = 1,
  n_max = 32
) %>% filter(`Gas/Land-Use Category` == 'Carbon Stock Change (CO2)a')


lulucf_co2_hist_long <- lulucf_co2_hist %>%
  pivot_longer(cols = 2:34, names_to = 'year') %>%
  select(year, value)

lulucf_proj <- read_xlsx("data-extra/USDA NFS Raw Data/LULUCF projections DRAFT compilation 82924.xlsx",
                        sheet = "LULUCF TABLE FOR PIPELINE") %>%
  filter(variable == 'Emissions|LULUCF|Carbon Stock Change') %>%
  pivot_longer(cols = 6:11, names_to = 'year') %>%
  select(year, value)

lulucf_plot_data <- lulucf_co2_hist_long %>% rbind(lulucf_proj) %>%
  mutate(
    year = as.numeric(year),
    value = as.numeric(value)
  ) %>%
  filter(year <= 2050, year >= 2000)


```

```{r}
lulucf_plot_proj <- lulucf_plot_data %>%
  filter(year >= 2022) %>%
  group_by(year) %>%
  mutate(min = min(value),
         max = max(value))

lulucf_plot_hist <- lulucf_plot_data %>% filter(year < 2025)
color_id <- '#0097FF'

lulucf_fig <- ggplot(mapping = aes(x = year, y = value)) +
  geom_line(data = lulucf_plot_hist, color = color_id,size = 0.7) +
  geom_ribbon(data = lulucf_plot_proj, aes(ymin = min, ymax = max),color = color_id, fill = color_id, alpha = 0.4,
              size = 0.7) +
 # geom_point(data = lulucf_plot_data, color = color_id) +
  labs(y = expression(paste("MMt C", O[2]))) +
  geom_vline(
    xintercept = 2022,
    linetype = 'dashed',
    color = "black",
    # size = 0.4,
    alpha = 0.5
  ) +
  scale_x_continuous(breaks = c(2000, 2005, 2010, settings$base_year, 2025, 2030, 2035, 2040,2045,2050),expand = c(0,0)) +
  expand_limits(y = c(0,-1500)) +
  scale_y_continuous(labels = scales::comma, breaks = c(0,-500,-1000,-1500)) +
  theme_btr()
lulucf_fig

```
```{r}
filename <- paste0("lulucf_fig_", Sys.Date(), ".png")
ggsave(paste0('output/', settings$version, "/tables_figs/to2050/lulucf/", filename),
  create.dir = TRUE,
  height = 4.5)
```

