---
pagetitle: "2024 Biennial Transparency Report Projections Chapter: Historical and Projected GHG Tables & Figures"
output:
  html_document:
    number_sections: false
    highlight: tango
    fontsize: 12
    fig_caption: false
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
params:
  mode: "interactive"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", fig.width = 9, fig.height = 7)


``` 

```{r}
source('packages.R')
library(targets)
library(tarchetypes)
tar_source()
source("scripts/theming.R")
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm,
    total_gross_emissions,
    ghgi_comp_tab,
    projections_ghgi,
    past_proj,
    kaya_comparison50,
    figmap_nrgco2_stackbar,
    figmap_sens_timeseries
    )
  )

projections_all_sm_nosens <- projections_all_sm %>%
  filter(grouping %in% c("ghgi","wm"))

projections_all_sm <- projections_all_sm %>%
  mutate(grouping = case_when(grouping == "wm" ~ "wm_sens",
                              TRUE~grouping))
```

# BTR Tables and Figures: BRVS & BTR Sensitivities Comparison

## Value Summary Tables {.tabset}

### Gas

```{r gas summary}
gas_df <- create_summary_table('gas','wm_sens', projections_all_sm, config, settings)
gas_table <- create_html_table(gas_df, 'Gas', settings)
gas_table_merged <- create_html_table_merged(gas_df, 'Gas', settings)

gas_table_merged
```

```{r}
filename <- paste0("gas_table_",Sys.Date(),".png")
gtsave(gas_table_merged, paste0('output/',settings$version,"/tables_figs_sens/results_tables/by_gas_sector/",filename))
```

### Sector

```{r sector summary}
sector_df <- create_summary_table('usproj_sector', 'wm_sens', projections_all_sm, config, settings)
sector_table <- create_html_table(sector_df, 'Sector', settings)
sector_table_merged <- create_html_table_merged(sector_df, 'Sector', settings)

sector_table_merged
```

```{r}
filename <- paste0("sector_table_",Sys.Date(),".png")
gtsave(sector_table_merged, paste0('output/',settings$version,"/tables_figs_sens/results_tables/by_gas_sector/",filename))
```
### % Change: Gas

```{r, pct change by gas}
pct_change_table_gas <- create_pct_change_table('gas', 'wm_sens', projections_all_sm, config, settings)
pct_change_html_gas_merged <- create_html_table_merged_pct_change(pct_change_table_gas, 'Gas', settings)

pct_change_html_gas_merged
```

### % Change: Sector

```{r, pct change by sector}
pct_change_table_sector <- create_pct_change_table('usproj_sector', 'wm_sens', projections_all_sm, config, settings)
pct_change_html_sector_merged <- create_html_table_merged_pct_change(pct_change_table_sector, 'Sector', settings)

pct_change_html_sector_merged
```


```{r}
tar_load(c(lulucf_data_extra_xlsx,
        lulucf_btr_crosswalk))

ctf_table <- make_btr_ctf_table(lulucf_data_extra_xlsx, lulucf_btr_crosswalk, projections_all_sm, settings, config)

write_csv(ctf_table, paste0("output/",settings$version,"/proj_tables/ctf_table7.csv"))
```


## Net-GHG Emissions {.tabset}

### WM_sens vs. No Sens.

```{r}
brvs_tne <- read_csv("data-extra/BR Voluntary Supplement 2023/brvs_totalnetemissions.csv")

```


```{r}
fig <- br_project_sens_nosens(projections_ghgi, config, settings)

fig
```

```{r}
filename <- paste0("btr_main_fig_nosens",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs_sens/btr_main_figs/main_fig/",filename), create.dir = TRUE, height = 7, width = 9)
```

### BR:VS - All Models

```{r}
fig <- br_project_brvs_sens(projections_ghgi, brvs_tne, config, settings, brvs_btr_subset = FALSE)

fig
```

### WM, WM_sens, BR:VS - All Models

```{r}
br_project_brvs_sens_wm(projections_ghgi, brvs_tne, config, settings, brvs_btr_subset = FALSE)
```


### No BR:VS

```{r}
fig <- br_project_sens(projections_ghgi, config, settings)

fig

```

```{r}
filename <- paste0("btr_main_fig_nobrvs_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs_sens/btr_main_figs/main_fig/",filename), create.dir = TRUE)
```


## Kaya BR5:VS Comparison

```{r}
kaya_fig <- kaya_brvs(kaya_comparison50, data_long_clean, config, settings)
kaya_fig
```

```{r}
ggsave(paste0('output/',settings$version,"/tables_figs_sens/kaya/kaya_singlepanel.png"), width = 5, create.dir = TRUE)

```


## GDP-Breakout, BR5:VS Comparison

```{r}
fig <- gdp_breakout(data_long_clean, config)

fig
```


# Sector Analysis {.tabset}

## Buildings {.tabset}

### All Models

```{r}
brvs_sectors <- read_csv("data-extra/BR Voluntary Supplement 2023/brvs_sectors.csv")
```


```{r}
buildings <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Buildings|Total", brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings, data_long_clean)

buildings
```

### BTR Subset

```{r}
buildings <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Buildings|Total", brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

buildings
```

## Electricity {.tabset}

### All Models

```{r}
electricity <- brvs_sens_sectors("Emissions|CO2|Energy|Supply|Electricity", brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

electricity
```

### BTR Subset

```{r}
electricity <- brvs_sens_sectors("Emissions|CO2|Energy|Supply|Electricity", brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

electricity
```

## Transportation {.tabset}

### All Models

```{r}
transportation <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Transportation|Total", brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

transportation
```

### BTR Subset

```{r}
transportation <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Transportation|Total", brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

transportation
```

## Industry {.tabset}

### All Models

```{r}
industry <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total", brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

industry
```

### BTR Subset

```{r}
industry <- brvs_sens_sectors("Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total", brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

industry
```

# Energy and Transportation CO2 Emissions Range {.tabset}

## Figure: Sens

```{r}
nrg_emissions <- projections_all_sm %>%
  filter(usproj_sector %in% c('Energy','Transportation') & gas == "CO2") %>%
  filter(grouping %in% c('ghgi','wm_sens')) %>%
  group_by(proj_name, year, grouping) %>%
  summarise(nrg_trn_co2 = sum(sum)) %>%
  filter(year %in% config$annual_1990_fives) 

ghgi <- nrg_emissions %>%
  filter(year <= settings$base_year,
         year >= 2005)

proj <- nrg_emissions %>%
  group_by(year) %>% 
  filter(year >= settings$base_year)%>%
    summarise(ymax = max(nrg_trn_co2),
              ymin = min(nrg_trn_co2),
              med = median(nrg_trn_co2),
              .groups = 'drop')

# nrg_05_comp <- nrg_emissions %>%
#   group_by(year) %>%
#   # summarise(max = max(nrg_trn_co2),
#   #           min = min(nrg_trn_co2))
#    # mutate(pct_change_05 = nrg_trn_co2/nrg_trn_co2[year==2005])

nrg_color <- "#2EAD96"

fig <- 
  ggplot() +
  geom_line(ghgi, mapping = aes(x = year, y = nrg_trn_co2, color = proj_name), color = 'black', size = 0.7) +
  geom_ribbon(proj, mapping = aes(x = year,ymax = ymax, ymin = ymin),
              color = nrg_color,
              fill = nrg_color,
              alpha = 0.4 ,
              size = 0.7)+
    labs(x = 'Year',
         y = expression(paste("Energy and Transportation Emissions (MMt ", CO[2], ")", sep = ""))) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(breaks = c(seq(1990,2020,by=5), 2022, seq(2025,2040,by=5)), expand = c(0,0)) +
    theme_btr() 
  
fig
```

```{r}
filename <- paste0("nrg_emissions_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs_sens/nrg_emissions/",filename), create.dir = TRUE,height = 5)
```


## Figure: No Sens

```{r}
nrg_emissions <- projections_all_sm %>%
  filter(usproj_sector %in% c('Energy','Transportation') & gas == "CO2") %>%
  filter(grouping %in% c('ghgi','wm_sens')) %>%
  group_by(proj_name, year, grouping) %>%
  summarise(nrg_trn_co2 = sum(sum)) %>%
  filter(year %in% config$annual_1990_fives)

nrg_emissions_nosens <- projections_all_sm_nosens %>%
  filter(usproj_sector %in% c('Energy','Transportation') & gas == "CO2") %>%
  filter(grouping %in% c('ghgi','wm')) %>%
  group_by(proj_name, year, grouping) %>%
  summarise(nrg_trn_co2 = sum(sum)) %>%
  filter(year %in% config$annual_1990_fives)

ghgi <- nrg_emissions %>%
  filter(year <= settings$base_year)

proj <- nrg_emissions %>%
  group_by(year) %>% 
  filter(year >= settings$base_year)%>%
    summarise(ymax = max(nrg_trn_co2),
              ymin = min(nrg_trn_co2),
              med = median(nrg_trn_co2),
              .groups = 'drop') %>%
  mutate(grouping = "2024 Policy Baseline")

proj_nosens <- nrg_emissions_nosens %>%
  group_by(year) %>% 
  filter(year >= settings$base_year)%>%
    summarise(ymax = max(nrg_trn_co2),
              ymin = min(nrg_trn_co2),
              med = median(nrg_trn_co2),
              .groups = 'drop') %>%
  mutate(grouping = "2024 Policy Baseline, No Sens.")

proj_final <- proj %>%
  rbind(proj_nosens)

# nrg_05_comp <- nrg_emissions %>%
#   group_by(year) %>%
#   # summarise(max = max(nrg_trn_co2),
#   #           min = min(nrg_trn_co2))
#    # mutate(pct_change_05 = nrg_trn_co2/nrg_trn_co2[year==2005])

nrg_color <- "#2EAD96"

fig <- 
  ggplot() +
  geom_line(ghgi, mapping = aes(x = year, y = nrg_trn_co2, color = proj_name), color = "black") +
  geom_ribbon(proj_final, mapping = aes(x = year,
                                        ymax = ymax,
                                        ymin = ymin,
                                        #color = grouping,
                                        fill = grouping),
              alpha = 0.6,
              size = 0.7)+
    labs(x = 'Year',
         y = expression(paste("MMt ", CO[2], sep = ""))) +
    geom_vline(
      xintercept = 2022,
      linetype = 'dashed',
      color = "black",
      # size = 0.4,
      alpha = 0.5) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(breaks = c(seq(1990,2020,by=5), 2022, seq(2025,2040,by=5)), expand = c(0,0))  +
    theme_btr() +
  scale_subpalette_single(unique(proj_final$grouping)) +
    theme(
      legend.position = "inside",
      legend.position.inside = c(0.2, 0.2))
  
fig
```

```{r}
filename <- paste0("nrg_emissions_fig_nosens",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs_sens/nrg_emissions/",filename), create.dir = TRUE,height = 4.5)
```

# LULUCF Sink Range {.tabset}

```{r}
# TODO: update to USDA NFS Raw Data/ ....FREEZE..... FOREST-ONLY CO2 tab for both historical and projections data for FORST ONLY CO2
lulucf_co2 <- read_xlsx(
  "data-extra/USDA NFS Raw Data/LULUCF projections DRAFT compilation FREEZE 10 22 2024.xlsx",
  sheet = "FOREST-ONLY CO2")


lulucf_co2_long <- lulucf_co2 %>%
  pivot_longer(cols = 2:25, names_to = 'year') %>%
  mutate(year = as.numeric(year)) %>% 
  select(year, value)

lulucf_hist <- lulucf_co2_long %>%
  filter(year <= settings$base_year) %>%
  select(year, value) %>%
  distinct()

lulucf_proj <- lulucf_co2_long %>%
  group_by(year) %>%
  summarise(max = max(value),
            min = min(value)) %>%
  filter(year < 2045,
         year >= settings$base_year)
  
```

## Figure

```{r}

color_id <- '#0097FF'

lulucf_fig <- ggplot() +
  geom_line(data = lulucf_hist, aes(x = year, y = value), color = 'black', size = 0.7) +
  geom_ribbon(data = lulucf_proj, aes(x = year, ymin = min, ymax = max), color = color_id, fill = color_id, alpha = 0.4,
              size = 0.7) +
 # geom_point(data = lulucf_plot_data, color = color_id) +
  labs(y = expression(paste("MMt C", O[2]))) +
  # geom_vline(
  #   xintercept = 2022,
  #   linetype = 'dashed',
  #   color = "black",
  #   # size = 0.4,
  #   alpha = 0.5
  # ) +
  scale_x_continuous(breaks = c(2000, 2005, 2010, settings$base_year, 2025, 2030, 2035, 2040),expand = c(0,0)) +
  expand_limits(y = c(0,-1500)) +
  scale_y_continuous(labels = scales::comma, breaks = c(0,-500,-1000,-1500)) +
  labs(y = expression(paste("Forest Net ",CO[2]," Sequestration (MMt ", CO[2], ")", sep = ""))) +
  theme_btr() 
lulucf_fig
```

```{r}
filename <- paste0("lulucf_fig_", Sys.Date(), ".png")
ggsave(paste0('output/', settings$version, "/tables_figs_sens/lulucf/", filename),
  create.dir = TRUE,
  height = 4.5,
  width = 9)
```

```{r}
# ref <- lulucf_plot_data %>% filter(year == 2005) %>% pull(value)
# 
# lulucf_stats_data <- lulucf_plot_data %>%
#   filter(year %in% c(2005, 2022, 2025, 2030, 2035, 2040)) %>%
#   mutate(`2005` = ref) %>%
#   mutate(pct_change_05 = ((value-`2005`)/`2005`)) %>%
#   group_by(year) %>%
#   summarise(min = min(pct_change_05),
#             max = max(pct_change_05))
# 
# gt(lulucf_stats_data)
```

# NCBR Comp w/ BR:VS

```{r}
brvs_tge <- read_xlsx("data-extra/BR Voluntary Supplement 2023/totalgrossemissions.xlsx")

brvs_tge_clean <- brvs_tge %>%
  pivot_longer(cols = 2:36,
               names_to = 'Year') %>%
  mutate(Report = "2023 BR Voluntary Supplement") %>% 
  select(Report, Year, value)

past_proj_clean <- past_proj %>%
  select(Report, Year, Emissions) %>%
  rename(Value = Emissions) %>%
  filter(Year <= 2035)


tge_btr <- projections_all_sm %>% 
  filter(!gas == 'LULUCF Sink',
         grouping %in% c('wm_sens','ghgi')) %>%
  group_by(proj_name, grouping, year) %>%
  summarise(value = sum(sum),.groups = 'drop')

tge_base <- tge_btr %>%
  filter(year == settings$base_year) %>%
  rename(Report = grouping,
         Year = year) %>% 
  select(names(brvs_tge_clean))

brvs_ribbon <- brvs_tge_clean %>%
  filter(Year > settings$base_year) %>%
  rbind(tge_base) %>%
  group_by(Year) %>% 
  summarise(max = max(value),
            min = min(value)) %>%
  mutate(Report = "2023 BR Voluntary Supplement",
         Year = as.numeric(Year)) %>%
  select(Report, Year, min, max)

tge_all_long <- tge_btr %>%
  mutate(Report = 'btr_2024') %>%
  rename(Year = year,
         Value = value) %>% 
  select(names(past_proj_clean)) %>%
  rbind(past_proj_clean) %>%
  mutate(Year = as.numeric(Year),
         Report = case_when(Report == "btr_2024" ~ "2024 BTR",
                            Report == "car_2014" ~ "2014 CAR",
                            Report == "br_2016" ~ "2016 BR",
                            Report == "br_2021" ~ "2021 BR",
                            Report == "br_2022" ~ "2022 BR"))
#%>%
 # filter(year %in% config$fives_proj_sm)


ncbr_comp_ribbon <- tge_all_long %>% 
  group_by(Report,Year) %>%
  mutate(min = min(Value),
         max = max(Value)) %>%
  select(Report,Year,min,max) %>%
  distinct()
# %>%rbind(brvs_ribbon)
```

```{r}
fig <- ncbr_comparison_figure_sens(ncbr_comp_ribbon, tge_all_long, settings, config)

fig
```

```{r}
filename <- paste0("ncbr_comp_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs_sens/ncbr_comparison/",filename), create.dir = TRUE,width = 9,height = 7)
```

## NCBR Table

```{r}
# Load in past NCBR data
past_proj_clean <- past_proj %>%
  select(Report, Year, Emissions) %>%
  rename(Value = Emissions) %>%
  filter(Year <= 2035)

past_proj_clean_hilow <- past_proj_clean %>%
  group_by(Report,Year) %>%
  mutate(low = min(Value),
         high = max (Value),
         Report = case_when(Report == "btr_2024" ~ "2024 BTR",
                            Report == "car_2014" ~ "2014 CAR",
                            Report == "br_2016" ~ "2016 BR",
                            Report == "br_2021" ~ "2021 BR",
                            Report == "br_2022" ~ "2022 BR")) %>%
  select(Report,Year,low,high)
```

```{r}
col_order <- c('category', 'year', 'low', 'high')
category <- 'gas'
group <- 'wm_sens'

summary <- projections_all_sm %>%
  rename(category = .data[[category]]) %>%
  filter(grouping %in% c(group,'ghgi')) %>%
  filter(year %in% config$seq_ncbr_comp_sm) %>%
  group_by(proj_name, category, year) %>%
  summarise(cat_sum = sum(sum), .groups = 'drop')

summary_total_gross <- summary %>%
  filter(!category == 'LULUCF Sink') %>%
  group_by(proj_name, year) %>%
  summarise(value = sum(cat_sum), .groups = 'drop') %>%
  group_by(year) %>%
  mutate(low = min(value), high = max(value)) %>%
  select(year, low, high) %>%
  distinct() %>%
  mutate(category = 'Total Gross Emissions') %>%
  select(all_of(col_order)) %>%
  rename(Projection = category) %>%
  mutate(Projection = '2024 BTR')

tge_all_long_high_low <- summary_total_gross %>%
  rename(Report = Projection,
         Year = year) %>%
  rbind(past_proj_clean_hilow) %>%
  filter(Year %in% config$seq_ncbr_comp_sm) %>%
  drop_na() %>%
  rename(Publication = Report)

proj_years <- c('2025', '2030', '2035', '2040')
hist_years <- c('2005', '2010', '2015', '2020')

proj_col_order <- c(
  '2025_low',
  '2025_high',
  '2030_low',
  '2030_high',
  '2035_low',
  '2035_high',
  '2040_low',
  '2040_high'
)

df_low <- tge_all_long_high_low %>%
  select(Publication, Year, low) %>%
  pivot_wider(names_from = 'Year', values_from = 'low')


df_high <- tge_all_long_high_low %>%
  select(Publication, Year, high) %>%
  pivot_wider(names_from = 'Year', values_from = 'high')

df_merged <- merge(df_low[, c('Publication', proj_years)],
                   df_high[, c('Publication', proj_years)],
                   by = 'Publication',
                   suffix = c('', '_high'))

for (year in proj_years) {
  colnames(df_merged)[colnames(df_merged) == year] <- paste0(year, '_low')
  colnames(df_merged)[colnames(df_merged) == paste0(year, '_high')] <- paste0(year, '_high')
}

df_merge_final <- merge(df_low %>% select(Publication, all_of(hist_years)), df_merged) %>%
  select(Publication, all_of(hist_years), all_of(proj_col_order)) %>%
  mutate_if(is.numeric, round)

numeric_cols <- sapply(df_merge_final, is.numeric)
df_merge_final[, numeric_cols] <- lapply(df_merge_final[, numeric_cols], scales::comma)

ncbr_table_df <- df_merge_final
for (col in names(ncbr_table_df)) {
  ncbr_table_df <- ncbr_table_df %>%
    mutate(col = as.character(col)) %>%
    select(names(df_merge_final)) %>%
    arrange(desc(Publication))
}
```

### Table

```{r}
proj_col_order <- c('2025', '2030', '2035', '2040')

stubhead <- 'Publication'

merged = ncbr_table_df %>%
  mutate(
    `2025` = case_when(
      `2025_low` == `2025_high` ~ `2025_high`,
      `2025_low` != `2025_high` ~ paste0(`2025_low`, " - ", `2025_high`)
    ),
    `2030` = case_when(
      `2030_low` == `2030_high` ~ `2030_high`,
      `2030_low` != `2030_high` ~ paste0(`2030_low`, " - ", `2030_high`)
    ),
    `2035` = case_when(
      `2035_low` == `2035_high` ~ `2035_high`,
      `2035_low` != `2035_high` ~ paste0(`2035_low`, " - ", `2035_high`)
    ),
    `2040` = case_when(
      `2040_low` == `2040_high` ~ `2040_high`,
      `2040_low` != `2040_high` ~ paste0(`2040_low`, " - ", `2040_high`)
    )
  ) %>%
  select(-contains("_"))

bold1 = nrow(merged) - 3
bold2 = nrow(merged) - 1
bold3 = nrow(merged) - 5

ncbr_comp_table <- merged %>%
  
  gt() %>%
  cols_align('center', columns = everything()) %>%
  cols_align('left', columns = stubhead) %>%
  # tab_style(
  #   style = cell_borders(
  #     color = "#1F77AE",
  #     sides = c("bottom"),
  #     weight = px(2)
  #   ),
  #   #
  #   locations = cells_body(rows = c(bold1, bold2, bold3))
  # ) %>% 

  
  gt_theme_nc_blue()

ncbr_comp_table
```

```{r}
filename <- paste0("ncbr_comp_table_",Sys.Date(),".png")
gtsave(ncbr_comp_table, paste0('output/',settings$version,"/tables_figs_sens/results_tables/ncbr_comparison/",filename))
```

# Sector Analysis: Combine WM & WM_sens {.tabset}

## Buildings {.tabset}

### All Models

```{r}
brvs_sectors <- read_csv("data-extra/BR Voluntary Supplement 2023/brvs_sectors.csv")
```


```{r}
buildings <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Buildings|Total", brvs_show = FALSE, brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings, data_long_clean)

buildings

ggsave(plot = buildings,filename = paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/buildings_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 4.5, width = 9)
```

### BTR Subset

```{r}
buildings <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Buildings|Total", brvs_show = TRUE, brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

buildings
```

## Electricity {.tabset}

### All Models

```{r}
electricity <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Supply|Electricity", brvs_show = FALSE, brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/electricity_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 4.5, width = 9)

electricity
```

### BTR Subset

```{r}
electricity <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Supply|Electricity", brvs_show = TRUE, brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

electricity
```

## Transportation {.tabset}

### All Models

```{r}
transportation <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Transportation|Total", brvs_show = FALSE, brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/transportation_comparison",Sys.Date(),".png"), height = 4.5, width = 9)

transportation
```

### BTR Subset

```{r}
transportation <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Transportation|Total", brvs_show = TRUE, brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

transportation
```

## Industry {.tabset}

### All Models

```{r}
industry <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total", brvs_show = FALSE, brvs_btr_subset = FALSE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/industry_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 4.5, width = 9)

industry
```

### BTR Subset

```{r}
industry <- brvs_wm_sens_combo_sectors("Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total", brvs_show = TRUE,  brvs_btr_subset = TRUE, brvs_sectors, ghgi_comp_tab, config, settings,data_long_clean)

industry
```

# Sector Analysis: Only Ribbons {.tabset}

## Buildings {.tabset}


```{r}
buildings <- br_sectors_sens(
  "Emissions|CO2|Energy|Demand|Buildings|Total",
  data_long_clean,
  ghgi_comp_tab,
  config,
  settings,
  expression(paste("Buildings Emissions (MMt C", O[2], ")"))
)

buildings

ggsave(plot = buildings,filename = paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/only_ribbons/buildings_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 5, width = 9)
```



## Electricity {.tabset}


```{r}
electricity <- br_sectors_sens(
  "Emissions|CO2|Energy|Supply|Electricity",
  data_long_clean,
  ghgi_comp_tab,
  config,
  settings,
  expression(paste("Electricity Emissions (MMt C", O[2], ")"))
)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/only_ribbons/electricity_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 5, width = 9)

electricity
```


## Transportation {.tabset}


```{r}
transportation <- br_sectors_sens(
  "Emissions|CO2|Energy|Demand|Transportation|Total",
  data_long_clean,
  ghgi_comp_tab,
  config,
  settings,
  expression(paste("Transportation Emissions (MMt C", O[2], ")"))
)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/only_ribbons/transportation_comparison",Sys.Date(),".png"), height = 5, width = 9)

transportation
```


## Industry {.tabset}


```{r}
industry <- br_sectors_sens(
  "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
  data_long_clean,
  ghgi_comp_tab,
  config,
  settings,
  expression(paste("Industry and Fuel Production Emissions (MMt C", O[2], ")"))
)

ggsave(paste0('output/',settings$version,"/tables_figs_sens/sector_analysis/only_ribbons/industry_comparison",Sys.Date(),".png"), create.dir = TRUE, height = 5, width = 9)

industry
```



# Stats

## Buildings Emissions Reductions - Direct and Indirect 

```{r}
BuildEmiss <- data_long_clean %>% 
  filter(variable %in% c("Emissions|CO2|Energy|Demand|Buildings",
                         "Emissions|CO2|Energy|Demand|Buildings|Indirect",
                         "Emissions|CO2|Energy|Demand|Buildings|Total") &
           scenario %in% config$scen_wm_sensitivities &
           model!= "EPA-GHGI") %>% 
  left_join(data_long_clean %>% 
              filter(variable %in% c("Emissions|CO2|Energy|Demand|Buildings",
                                     "Emissions|CO2|Energy|Demand|Buildings|Indirect",
                                     "Emissions|CO2|Energy|Demand|Buildings|Total") &
                       scenario %in% config$scen_wm_sensitivities &
                       model == "EPA-GHGI" &
                       year == 2005) %>% 
              select(variable, base = value)) %>% 
  mutate(reduction = 1- (value/base)) %>% 
  filter(year %in% c(2025,2030,2035,2040)) %>% 
  select(model, year, variable, reduction)

Indirect <- BuildEmiss %>% 
  filter(variable == "Emissions|CO2|Energy|Demand|Buildings|Indirect") %>% 
  mutate(variable = "Indirect") %>% 
  pivot_wider(names_from = year,
              values_from = reduction)

Direct <- BuildEmiss %>% 
  filter(variable == "Emissions|CO2|Energy|Demand|Buildings") %>% 
  mutate(variable = "Direct") %>% 
  pivot_wider(names_from = year,
              values_from = reduction)

Total <- BuildEmiss %>% 
  filter(variable == "Emissions|CO2|Energy|Demand|Buildings|Total") %>% 
  mutate(variable = "Total") %>% 
  pivot_wider(names_from = year,
              values_from = reduction)

kable(Indirect)
kable(Direct)
kable(Total)
```

## Energy CO2 emissions reductions from 2005 - Direct {.tabset}

```{r}
elec <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Supply|Electricity',
  config,
  config$scen_wm_sensitivities
)

ghgi_ind_fp_dir_df <- ghgi_comp_tab %>%
    filter(model == config$model_hist) %>%
    filter(year %in% config$hist) %>%
    mutate(variable = case_when(
      variable == "Emissions|CO2|Energy|Demand|Industry" ~ "Emissions|CO2|Energy|Demand|Industry and Fuel Production",
      TRUE~variable
    )) %>%
    filter(variable == "Emissions|CO2|Energy|Demand|Industry and Fuel Production")



data_long_clean_ind_fp <- data_long_clean %>% rbind(ghgi_ind_fp_dir_df)

industry_and_fp_dir <- section_pct_change_05(
  data_long_clean_ind_fp,
  "Emissions|CO2|Energy|Demand|Industry and Fuel Production",
  config,
  config$scen_wm_sensitivities
)

industry_dir <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Industry',
  config,
  config$scen_wm_sensitivities
)

buildings <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings',
  config,
  config$scen_wm_sensitivities
)

transportation <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Transportation',
  config,
  config$scen_wm_sensitivities
)

buildings_res <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings|Residential',
  config,
  config$scen_wm_sensitivities
)

buildings_com <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings|Commercial',
  config,
  config$scen_wm_sensitivities
)
```

### Electricity

```{r}
elec_table <- create_stats_table(elec)
elec_table
```

### Industry and Fuel Prod - Direct

```{r}
industry_table <- create_stats_table(industry_and_fp_dir)
industry_table
```

### Industry direct

```{r}
industry_table <- create_stats_table(industry_dir)
industry_table
```

### Buildings
```{r}
buildings_table <- create_stats_table(buildings)
buildings_table
```

### Commercial
```{r}
buildings_com_table <- create_stats_table(buildings_com)
buildings_com_table
```

### Residential
```{r}
buildings_res_table <- create_stats_table(buildings_res)
buildings_res_table
```

### Transportation
```{r}
transportation_table <- create_stats_table(transportation)
transportation_table
```


## Energy CO2 emissions reductions from 2005 - Total Emissions {.tabset}

```{r}

ghgi_ind_fp_dir_df <- ghgi_comp_tab %>%
    filter(model == config$model_hist) %>%
    filter(year %in% config$hist) %>%
    mutate(variable = case_when(
      variable == "Emissions|CO2|Energy|Demand|Industry|Total" ~ "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
      TRUE~variable
    )) %>%
    filter(variable == "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total")



data_long_clean_ind_fp <- data_long_clean %>% rbind(ghgi_ind_fp_dir_df)

industry_and_fp_dir <- section_pct_change_05(
  data_long_clean_ind_fp,
  "Emissions|CO2|Energy|Demand|Industry and Fuel Production|Total",
  config,
  config$scen_wm_sensitivities
)

industry_dir <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Industry|Total',
  config,
  config$scen_wm_sensitivities
)

buildings <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings|Total',
  config,
  config$scen_wm_sensitivities
)

transportation <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Transportation|Total',
  config,
  config$scen_wm_sensitivities
)

buildings_res <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings|Residential|Total',
  config,
  config$scen_wm_sensitivities
)

buildings_com <- section_pct_change_05(
  data_long_clean,
  'Emissions|CO2|Energy|Demand|Buildings|Commercial|Total',
  config,
  config$scen_wm_sensitivities
)
```


### Industry and Fuel Prod

```{r}
industry_table <- create_stats_table(industry_and_fp_dir)
industry_table
```

### Industry

```{r}
industry_table <- create_stats_table(industry_dir)
industry_table
```

### Buildings
```{r}
buildings_table <- create_stats_table(buildings)
buildings_table
```

### Commercial

```{r}
buildings_com_table <- create_stats_table(buildings_com)
buildings_com_table
```

### Residential

```{r}
buildings_res_table <- create_stats_table(buildings_res)
buildings_res_table
```

### Transportation

```{r}
transportation_table <- create_stats_table(transportation)
transportation_table
```

## ZEV Shares {.tabset}

### Sales {.tabset}

#### Passenger

```{r}
zev_share_table(data_long_clean,"Energy Service|Transportation|Passenger|ZEV Sales Share", config$scen_wm_sensitivities)
```

#### Freight

```{r}
zev_share_table(data_long_clean,"Energy Service|Transportation|Freight|ZEV Sales Share", config$scen_wm_sensitivities)
```

#### Figure

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 43, "United States", scenario_rename = TRUE)
```

### Stock {.tabset}

#### Passenger

```{r}
zev_share_table(data_long_clean,"Energy Service|Transportation|Passenger|ZEV Stock Share", config$scen_wm_sensitivities)
```

#### Freight

```{r}
zev_share_table(data_long_clean,"Energy Service|Transportation|Freight|ZEV Stock Share", config$scen_wm_sensitivities)
```

#### Figure

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 44, "United States", scenario_rename = TRUE)
```

## Energy-Related Emissions Compared to 2005 {.tabset}

### CO2

```{r}
nrgco2 <- projections_all_sm %>%
  filter(grouping %in% c("wm_sens","ghgi")) %>%
  filter(year %in% c(2005, 2025, 2030, 2035, 2040)) %>%
  filter(gas == "CO2" & usproj_sector == "Energy") %>%
  select(proj_name,year,pct_change_05) %>%
  distinct()

nrgco2 <- nrgco2[order(nrgco2$year),]
  
nrgco2_wide <- nrgco2 %>%
  filter(!year == 2005) %>%
  pivot_wider(names_from = 'year', values_from = 'pct_change_05')

nrgco2_stats = data.frame(
  stat = c("min", "max"),
  "2025" = c(
    min(nrgco2_wide$`2025`, na.rm = TRUE),
    max(nrgco2_wide$`2025`, na.rm = TRUE)
  ),
  "2030" = c(
    min(nrgco2_wide$`2030`, na.rm = TRUE),
    max(nrgco2_wide$`2030`, na.rm = TRUE)
  ),
  "2035" = c(
    min(nrgco2_wide$`2035`, na.rm = TRUE),
    max(nrgco2_wide$`2035`, na.rm = TRUE)
  ),
  "2040" = c(
    min(nrgco2_wide$`2040`, na.rm = TRUE),
    max(nrgco2_wide$`2040`, na.rm = TRUE)
  )
)

names(nrgco2_stats) = names(nrgco2_wide)

nrgco2_stats_table <- create_stats_table(nrgco2_stats)
nrgco2_stats_table

nrgco2_table <- create_stats_table(nrgco2_wide)
nrgco2_table
```

### CH4

```{r}
nrgch4 <- projections_all_sm %>%
  filter(grouping %in% c("wm_sens","ghgi")) %>%
  filter(year %in% c(2005, 2025, 2030, 2035, 2040)) %>%
  filter(gas == "CH4" & usproj_sector == "Energy") %>%
  select(proj_name,year,pct_change_05) %>%
  distinct()

nrgch4 <- nrgch4[order(nrgch4$year),]
  
nrgch4_wide <- nrgch4 %>% 
    filter(!year == 2005) %>%
    pivot_wider(names_from = 'year',
                                values_from = 'pct_change_05')

nrgch4_stats = data.frame(
  stat = c("min", "max"),
  "2025" = c(
    min(nrgch4_wide$`2025`, na.rm = TRUE),
    max(nrgch4_wide$`2025`, na.rm = TRUE)
  ),
  "2030" = c(
    min(nrgch4_wide$`2030`, na.rm = TRUE),
    max(nrgch4_wide$`2030`, na.rm = TRUE)
  ),
  "2035" = c(
    min(nrgch4_wide$`2035`, na.rm = TRUE),
    max(nrgch4_wide$`2035`, na.rm = TRUE)
  ),
  "2040" = c(
    min(nrgch4_wide$`2040`, na.rm = TRUE),
    max(nrgch4_wide$`2040`, na.rm = TRUE)
  )
)

names(nrgch4_stats) = names(nrgch4_wide)

nrgch4_stats_table <- create_stats_table(nrgch4_stats)
nrgch4_stats_table
```

## buildings - res and com % electricity of total demand {.tabset}

### Commercial

```{r}
com_electrif <- data_long_clean %>%
  filter(scenario %in% config$scen_wm_sensitivities,
         variable %in% c("Final Energy|Buildings|Commercial|Percent Electricity"),
         year %in% config$table) %>%
  filter(year != 2022) %>%
  select(model, scenario, year, value)

com_electrif <- com_electrif[order(com_electrif$year),]

com_electrif_wide <- com_electrif %>% pivot_wider(names_from = 'year',
                                                  values_from = 'value')

com_electrif <- create_stats_table(com_electrif_wide)
com_electrif
```

### Residential

```{r}
res_electrif <- data_long_clean %>%
  filter(scenario %in% config$scen_wm_sensitivities,
         variable %in% c("Final Energy|Buildings|Residential|Percent Electricity"),
         year %in% config$table) %>%
  filter(year != 2022) %>%
  select(model, scenario, year, value)

res_electrif <- res_electrif[order(res_electrif$year),]

res_electrif_wide <- res_electrif %>% pivot_wider(names_from = 'year',
                                                  values_from = 'value')

res_electrif <- create_stats_table(res_electrif_wide)

res_electrif
```

## Percent clean energy

```{r}
vars = c("Secondary Energy|Electricity|Renewable","Secondary Energy|Electricity|Zero-Emissions",
         "Secondary Energy|Electricity")
df = data_long_clean %>%
  filter(model %in% config$model_wm) %>%
  filter(scenario %in% config$scen_wm_sensitivities) %>%
  filter(variable %in% vars) %>%
  mutate(variable = case_when(
    str_detect(variable, "Renew") ~ "renew",
    str_detect(variable, "Zero") ~ "zero",
    TRUE~"total"
  )) %>%
  filter(year %in% c(2025,2030,2035,2040)) %>%
  select(-region,-datasrc) %>%
  pivot_wider(names_from = "variable", values_from = "value") %>%
  mutate(pct_renew = renew/total,
         pct_zero = zero/total) %>%
  pivot_longer(cols = 5:9, names_to = "variable", values_to = "value") %>%
  pivot_wider(names_from = "year", values_from = "value")
```

### Percent Renewable
```{r}
pct_renew = df %>% filter(variable == "pct_renew")
gt(pct_renew)
```

### Percent Zero-Emissions
```{r}
pct_zero = df %>% filter(variable == "pct_zero")
gt(pct_zero)
```

# Ad-hoc tables/figs

Buildings and electricity emissions reductions in 2040 compared to 2005

```{r}
get_value_breakout <- function(data_long_clean, var_list, config) {
  
data_wm_usa <- data_long_clean %>% filter(scenario %in% config$scen_wm_sensitivities,
                                             region == 'United States')

var_df <- data_wm_usa %>% filter(variable %in% var_list)

var_df_clean <- var_df %>%
  select(model, scenario, year, variable, value) %>%
  filter(year %in% config$fives_sumtab) %>%
  distinct() %>%
  mutate(across(where(is.numeric), round, 2))
return(var_df_clean)
}

```
```{r}
# var_list <- c('Emissions|CO2|Energy|Demand|Buildings',
#               'Emissions|CO2|Energy|Supply|Electricity')
# 
# be_df <- get_value_breakout(data_long_clean, var_list, config)
# be_df2 = be_df %>% 
#   pivot_wider(names_from = year,
#               values_from = value) %>% 
#   group_by(variable) %>% 
#   rename(base ="2005",
#          target = "2040") %>% 
#   mutate(reduction =1 - (target/max(base, na.rm = "yes"))) %>% 
#   ungroup() %>% 
#   filter(model != "EPA-GHGI") %>% 
#   select(model,variable,reduction) %>% 
#   pivot_wider(names_from = model,
#               values_from = reduction)
# 
# grid.table(be_df2)
```

Share of fuel usage in Residential Buildings

```{r}
# var_list <- c('Final Energy|Buildings|Residential|Electricity',
#                'Final Energy|Buildings|Residential|Gas',
#                'Final Energy|Buildings|Residential')
# 
# br_df <- get_value_breakout(data_long_clean, var_list, config)
# 
# br_df2 <- br_df %>%
#   filter(variable != "Final Energy|Buildings|Residential") %>% 
#   left_join(br_df %>% 
#               filter(variable == "Final Energy|Buildings|Residential") %>%
#               select(-variable) %>% 
#               rename(total = value)) %>% 
#   mutate(Share = value/total) %>% 
#   select(-value,-total) %>% 
#   filter(year == 2040) %>% 
#   pivot_wider(names_from = model,
#               values_from = Share)
# 
# grid.table(br_df2)
```

Share of fuel usage in Commercial Buildings

```{r}
# var_list <-  c('Final Energy|Buildings|Commercial|Electricity',
#                'Final Energy|Buildings|Commercial|Gas',
#                'Final Energy|Buildings|Commercial')
# 
# bc_df <- get_value_breakout(data_long_clean, var_list, config)
# 
# bc_df2 = bc_df %>%
#   filter(variable != "Final Energy|Buildings|Commercial") %>% 
#   left_join(bc_df %>% 
#               filter(variable == "Final Energy|Buildings|Commercial") %>%
#               select(-variable) %>% 
#               rename(total = value)) %>% 
#   mutate(Share = value/total) %>% 
#   select(-value,-total) %>% 
#   filter(year == 2040) %>% 
#   pivot_wider(names_from = model,
#               values_from = Share)
# 
# grid.table(bc_df2)
```

Share of Wind and Solar in elec gen in 2040

```{r}
tar_load(figmap_nrgco2_stackbar)
df <- figmap_nrgco2_stackbar %>% filter(figure_no == 13)

var_list <- df$variable

eg_df <- get_value_breakout(data_long_clean, var_list, config)
  
```

```{r}
var_list <- c('Secondary Energy|Electricity|Wind','Secondary Energy|Electricity|Solar','Secondary Energy|Electricity')
sw_df <- get_value_breakout(data_long_clean, var_list, config)

sw_df2 = sw_df %>% 
  filter(variable %in% c('Secondary Energy|Electricity|Wind','Secondary
                         Energy|Electricity|Solar')) %>% 
  group_by(model,year,scenario) %>% 
  summarise(value = sum(value)) %>% 
  left_join(sw_df %>% 
              filter(variable == 'Secondary Energy|Electricity') %>% 
              select(-variable) %>% 
              rename(total = value)) %>% 
  mutate(Share = value/total) %>% 
  select(-value,-total) %>% 
  filter(year %in% c(2040)) %>% 
  pivot_wider(names_from = model,
              values_from = Share)

grid.table(sw_df2)
```

```{r}
tar_load(figmap_sens_stackbar)
df <- data_from_graph("stacked_bar", config, data_long_clean, figmap_sens_stackbar, 3, "United States")

df_total <- df %>%
  group_by(model,year,scenario) %>%
  summarise(total = sum(value)) %>%
  pivot_wider(names_from = 'year',
              values_from = 'total')

df_total_var <- df %>%
  group_by(model,variable,year) %>%
  summarise(total = sum(value)) %>%
  pivot_wider(names_from = 'year',
              values_from = 'total')
```


Reduction in coal to electricity in 2040 compared to model's EIA 2023

```{r}
# var_list <- 'Secondary Energy|Electricity|Input|Coal'
# 
# pec_df <- get_value_breakout(data_long_clean,var_list, config)
# 
# Coal2023 = 7241.636*1000000000000*1.05506e-15
# 
# pec_df2 = pec_df %>% 
#   pivot_wider(names_from = year,
#               values_from = value) %>% 
#   rename(base ="2020",
#          target = "2040") %>% 
#   mutate(reduction =1 - (target/Coal2023)) %>% 
#   select(model,variable,reduction) %>% 
#   pivot_wider(names_from = model,
#               values_from = reduction)
# 
# grid.table(pec_df2)
```

Passenger Vehicle sales share in 2040

```{r}
# var_list <- c("Energy Service|Transportation|Passenger|BEV|Sales Share",
#               "Energy Service|Transportation|Passenger|FCEV|Sales Share",
#               "Energy Service|Transportation|Passenger|PHEV|Sales Share",
#               "Energy Service|Transportation|Passenger|ICE|Sales Share")
# 
# vs_df <- get_value_breakout(data_long_clean, var_list, config)
# 
# vs_df2 = vs_df %>% 
#   filter(year ==2040) %>% 
#   pivot_wider(names_from = model,
#               values_from = value) 
# 
# grid.table(vs_df2)
  
```

Freight Vehicle sales share in 2040

```{r}
# var_list <- c("Energy Service|Transportation|Freight|BEV|Sales Share",
#               "Energy Service|Transportation|Freight|FCEV|Sales Share",
#               "Energy Service|Transportation|Freight|PHEV|Sales Share",
#               "Energy Service|Transportation|Freight|ICE|Sales Share")
# 
# vs_df <- get_value_breakout(data_long_clean, var_list, config)

# vs_df2 = vs_df %>% 
#   filter(year ==2040) %>% 
#   spread(model,value) 

# grid.table(vs_df2)
```


