---
title: "Comparison of BTR1 With Measures and LEEP Projections"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_leepcompare_timeseries
    )
  )
```

```{r}
source('packages.R')
source("scripts/theming.R")
```

# Energy CO2 Emissions {.tabset}

## Sector 

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 9, "United States", scenario_rename = FALSE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
model
```

## Fuel

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 30, "United States")
model
```

# Energy Consumption

## Final Energy {.tabset}

### Fuel 

```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 1, "United States", scenario_rename = FALSE)
Fuel
```

### Fuel - Zoom

```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 24, "United States", scenario_rename = FALSE)
Fuel
```

### Sector 

```{r}
Sector = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 2, "United States", scenario_rename = FALSE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
Sector
```

## Sectoral Detail {.tabset}

### Buildings Total

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 17, "United States", scenario_rename = FALSE,
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy"))
Buildings_bymodel
```

### Residential

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 31, "United States", scenario_rename = FALSE)
Buildings_bymodel
```

### Commercial 

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 32, "United States", scenario_rename = FALSE)
Buildings_bymodel
```

### Industry 

```{r}
Industry_bymodel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 18, "United States", scenario_rename = FALSE)
Industry_bymodel
```

### Transportation 

```{r}
Transportation_bymodel = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 19, "United States", scenario_rename = FALSE)
Transportation_bymodel
```

## Percent Electricity

```{r}
Percent_Electricity = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 14, "United States", scenario_rename = FALSE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
Percent_Electricity
```

# Energy Production

## Secondary Energy {.tabset}

### Model

```{r, fig.width=12}
Model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 8, "United States", scenario_rename = FALSE)
Model
```

### Model - Zoom

```{r}
Model_zoom = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 25, "United States", scenario_rename = FALSE)
Model_zoom

```

## Electricity Production {.tabset}

### Generation 

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 15, "United States", scenario_rename = FALSE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
elec_model

```

### Generation - Zoom

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 27, "United States", scenario_rename = FALSE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
elec_model

```

### Capacity 

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 16, "United States", scenario_rename = FALSE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
elec_model

```

### Capacity - Zoom

```{r}
elec_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 26, "United States", scenario_rename = FALSE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
elec_model
```

## Combustion {.tabset}

### Generation by Model

```{r, fig.width=12}
gen_by_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 20, "United States", scenario_rename = FALSE)
gen_by_model
```

### Generation by Model - Zoom

```{r}
gen_by_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 28, "United States", scenario_rename = FALSE)
gen_by_model
```

### Capacity by Model

```{r, fig.width=12}
cap_by_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 22, "United States", scenario_rename = FALSE)
cap_by_model
```

### Capacity by Model - Zoom

```{r}
cap_by_model = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 29, "United States", scenario_rename = FALSE)
cap_by_model
```

## Non-Combustion {.tabset}

### Generation by Model

```{r}
gen_by_model_nc = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 23, "United States", scenario_rename = FALSE)
gen_by_model_nc
```

### Capacity by Model

```{r}
cap_by_model_nc = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 21, "United States", scenario_rename = FALSE)
cap_by_model_nc
```


------------------------------------------------------------------------

# Model Comparision

## Input Assumptions {.tabset}

### Population

```{r}
pop = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 12, "United States", scenario_rename = FALSE)
pop
```

### GDP

```{r}
gdp = print_graph("time_series", config, data_long_clean, figmap_leepcompare_timeseries, 13, "United States", scenario_rename = FALSE)
gdp
```

