---
title: "BTR Results Overview"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r Sys.time()`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```


```{r}
library(targets)
library(tarchetypes)
tar_source()
```

```{r}
tar_load(config)
tar_load(settings)
tar_load(data_long_clean)
tar_load(figmap_nrgco2_stackbar)
tar_load(figmap_nrgco2_timeseries)
tar_load(figmap_nrgco2_diffbar)
tar_load(figmap_draftbriefing_stackbar)
```

```{r}
source('packages.R')
source("scripts/theming.R")
```

# Emissions

## Energy CO2 Emissions {.tabset}

### Sector

```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 19, "United States", scenario_rename = TRUE)
sector
```

### Model

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
model
```

# Energy Consumption

## Final Energy {.tabset}

### Fuel
```{r}
fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 14, "United States", scenario_rename = TRUE)
fuel
```

### Sector
```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 17, "United States", scenario_rename = TRUE)
sector
```


## Final Energy by Model {.tabset}

### Sector
```{r}
Sector = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 2, "United States", scenario_rename = TRUE)
Sector
```

### Fuel
```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 1, "United States", scenario_rename = TRUE)
Fuel
```


## Final Energy by Sector {.tabset}

### Buildings
```{r}
Buildings = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 8, "United States", scenario_rename = TRUE)
Buildings
```

### Industry
```{r}
Industry = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 9, "United States", scenario_rename = TRUE)
Industry
```

### Transportation
```{r}
Transportation = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 12, "United States", scenario_rename = TRUE)
Transportation
```

# Energy Production

## Secondary Energy {.tabset}

### Fuel
```{r}
Fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 15, "United States", scenario_rename = TRUE)
Fuel
```

### Model
```{r}
Model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 8, "United States", scenario_rename = TRUE)
Model
```

## Electricity Production {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 13, "United States", scenario_rename = TRUE)
elec_gen
```


### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 3, "United States", scenario_rename = TRUE)
Capacity
```



## Electricity Production - Combustion {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 6, "United States", scenario_rename = TRUE)
elec_gen
```


### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 4, "United States", scenario_rename = TRUE)
Capacity
```



## Electricity Production - Non-Combustion {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 7, "United States", scenario_rename = TRUE)
elec_gen
```


### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 5, "United States", scenario_rename = TRUE)
Capacity
```

---

# BTR Tables and Figures

```{r}
tar_load(c(projections_all_sm, config))
```

## Value Summary Tables {.tabset}

```{r create df}
gas_df <- create_summary_table('gas','wm', projections_all_sm, config)
sector_df <- create_summary_table('usproj_sector', 'wm', projections_all_sm, config)
```

### Gas
```{r gas summary}
gas_table <- create_html_table(gas_df, 'Gas',config)
gas_table
```


```{r}
filename <- paste0("gas_table_",Sys.Date(),".png")
gtsave(gas_table, paste0('output/',settings$version,"/tables_figs/results_tables/estimated_values/",filename))

```

### Sector
```{r sector summary}
sector_table <- create_html_table(sector_df, 'Sector',config)
sector_table
```

```{r}

filename <- paste0("sector_table_",Sys.Date(),".png")
gtsave(sector_table, paste0('output/',settings$version,"/tables_figs/results_tables/estimated_values/",filename))
```

## 2005 Percent Change Table {.tabset}

### Gas
```{r, pct change by gas}
pct_change_table_gas <- create_pct_change_table('gas', 'wm', projections_all_sm, config)
pct_change_html_gas <- create_pct_change_html_table(pct_change_table_gas, 'Gas', config)
pct_change_html_gas
```


```{r}

filename <- paste0("gas_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_gas, paste0('output/',settings$version,"/tables_figs/results_tables/percent_change_2005/",filename))
```

### Sector
```{r, pct change by sector}
pct_change_table_sector <- create_pct_change_table('usproj_sector', 'wm', projections_all_sm, config)
pct_change_html_sector <- create_pct_change_html_table(pct_change_table_sector, 'Sector', config)
pct_change_html_sector
```


```{r}

filename <- paste0("sector_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_sector, paste0('output/',settings$version,"/tables_figs/results_tables/percent_change_2005/",filename))
```

## BTR Main Plot {.tabset}

```{r data}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum)) %>%
  filter(year %in% config$fives)

ghgi = net_ghg %>% filter(proj_name == "ghgi")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == 2022,]$sum
baseline = ghgi[ghgi$year == 2005,]$sum

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = 2022,
    sum = ghgi$sum[ghgi$year == 2022])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c((baseline * (1-.169)), (baseline * (1-.26)), (baseline * (1-.50))),
  ymax = c((baseline * (1-.171)), (baseline * (1-.28)), (baseline * (1-.52))),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Net GHG Emissions
```{r proj function}
projections = br_project(ghgi, proj, targets = ndc_targets)
projections

#TODO: create a new figure that graphs the % reduction from 2005 instead of the objective values - both for historical emissions AND projections
```


```{r}

net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum),.groups = 'drop') %>%
  filter(year %in% config$fives) %>%
  mutate(pct_change_05 = round((sum/sum[year==2005]-1),2))


ghgi = net_ghg %>% filter(proj_name == "ghgi")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == 2022,]$pct_change_05
baseline = ghgi[ghgi$year == 2005,]$pct_change_05

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = 2022,
    pct_change_05 = ghgi$pct_change_05[ghgi$year == 2022])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c(-.17, -.28, -.52),
  ymax = c(-.17, -.26, -.5),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)




```

### Percent Change from 2005

```{r}
projections_pct_change = br_project_pct_change(ghgi, proj, targets = ndc_targets)
projections_pct_change
```

