---
title: "BTR Results Overview"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r Sys.time()`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm,
    figmap_nrgco2_stackbar,
    figmap_nrgco2_timeseries,
    figmap_nrgco2_diffbar
    )
  )
```

```{r}
source('packages.R')
source("scripts/theming.R")
```

# Emissions

## Energy CO2 Emissions by Sector {.tabset}

### Sector

```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 19, "United States", scenario_rename = TRUE)
sector
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,19)
figure_subset_vars <- unique(figure_subset_df$variable)
nrgco2_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, figure_subset_vars, data_long_clean, config)

buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Buildings", data_long_clean, config)
industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Industry", data_long_clean, config)
transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Transportation", data_long_clean, config)
```

In the "With Measures" scenarios, Energy CO~2~ emissions reductions range by model from 2020 to 2040:

-   GCAM: `r nrgco2_value_list[1]`%
-   OP-NEMS: `r nrgco2_value_list[2]`%
-   USREP-ReEDS: `r nrgco2_value_list[3]`%

### Model

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
model
```

By sector, emissions reductions are estimate to change from 2020 to 2040:

-   Buildings:
    -   GCAM: `r buildings_value_list[1]`%
    -   OP-NEMS: `r buildings_value_list[2]`%
    -   USREP-ReEDS: `r buildings_value_list[3]`%
-   Industry:
    -   GCAM: `r industry_value_list[1]`%
    -   OP-NEMS: `r industry_value_list[2]`%
    -   USREP-ReEDS: `r industry_value_list[3]`%
-   Transportation:
    -   GCAM: `r transportation_value_list[1]`%
    -   OP-NEMS: `r transportation_value_list[2]`%
    -   USREP-ReEDS: `r transportation_value_list[3]`%

## Energy CO2 Emissions by Fuel {.tabset}

### Fuel

```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 24, "United States", scenario_rename = TRUE)
sector
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,24)
figure_subset_vars <- unique(figure_subset_df$variable)
nrgco2_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, figure_subset_vars, data_long_clean, config)

buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Coal", data_long_clean, config)
industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Gas", data_long_clean, config)
transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Oil", data_long_clean, config)
```

### Model

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 30, "United States")
model
```

# Energy Consumption

## Final Energy {.tabset}

### Fuel

```{r}
fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 14, "United States", scenario_rename = TRUE)
fuel
```

### Fuel by Model

```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 1, "United States", scenario_rename = TRUE)
Fuel
```

### Fuel by Model - Zoom

```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 24, "United States", scenario_rename = TRUE)
Fuel
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,14)
figure_subset_vars <- unique(figure_subset_df$variable)
final_energy_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, figure_subset_vars, data_long_clean, config)

fe_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Coal", data_long_clean, config)
fe_electricity_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Electricity", data_long_clean, config)
fe_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Gas", data_long_clean, config)
fe_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Oil", data_long_clean, config)
```

Energy consumption is estimated to change from 2020 to 2040:

-   GCAM: `r final_energy_value_list[1]`%
-   OP-NEMS: `r final_energy_value_list[2]`%
-   USREP-ReEDS: `r final_energy_value_list[3]`%

By fuel-type, energy consumption is estimated to change from 2020 to 2040:

-   Coal:
    -   GCAM: `r fe_coal_value_list[1]`%
    -   OP-NEMS: `r fe_coal_value_list[2]`%
    -   USREP-ReEDS: `r fe_coal_value_list[3]`%
-   Electricity:
    -   GCAM: `r fe_electricity_value_list[1]`%
    -   OP-NEMS: `r fe_electricity_value_list[2]`%
    -   USREP-ReEDS: `r fe_electricity_value_list[3]`%
-   Gas:
    -   GCAM: `r fe_gas_value_list[1]`%
    -   OP-NEMS: `r fe_gas_value_list[2]`%
    -   USREP-ReEDS: `r fe_gas_value_list[3]`%
-   Oil:
    -   GCAM: `r fe_oil_value_list[1]`%
    -   OP-NEMS: `r fe_oil_value_list[2]`%
    -   USREP-ReEDS: `r fe_oil_value_list[3]`%

### Sector

```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 17, "United States", scenario_rename = TRUE)
sector
```

```{r}
fe_buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Buildings", data_long_clean, config)
fe_industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Industry", data_long_clean, config)
fe_transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Transportation", data_long_clean, config)

```

By sector, energy consumption is estimated to change from 2020 to 2040:

-   Buildings:
    -   GCAM: `r fe_buildings_value_list[1]`%
    -   OP-NEMS: `r fe_buildings_value_list[2]`%
    -   USREP-ReEDS: `r fe_buildings_value_list[3]`%
-   Industry:
    -   GCAM: `r fe_industry_value_list[1]`%
    -   OP-NEMS: `r fe_industry_value_list[2]`%
    -   USREP-ReEDS: `r fe_industry_value_list[3]`%
-   Transportation:
    -   GCAM: `r fe_transportation_value_list[1]`%
    -   OP-NEMS: `r fe_transportation_value_list[2]`%
    -   USREP-ReEDS: `r fe_transportation_value_list[3]`%

### Sector by Model

```{r}
Sector = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 2, "United States", scenario_rename = TRUE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
Sector
```

## Final Energy by Sector {.tabset}

### Buildings

```{r}
Buildings = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 8, "United States", scenario_rename = TRUE)
Buildings
```

### Buildings by Model

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 17, "United States", scenario_rename = TRUE,
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy"))
Buildings_bymodel
```

### Industry

```{r}
Industry = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 9, "United States", scenario_rename = TRUE)
Industry
```

### Industry by Model

```{r}
Industry_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 18, "United States", scenario_rename = TRUE)
Industry_bymodel
```

### Transportation
TODO: Add facets vehicle type sales share/stock share, tabs freight/passenger

```{r}
Transportation = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 12, "United States", scenario_rename = TRUE)
Transportation
```

### Transportation by Model

```{r}
Transportation_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 19, "United States", scenario_rename = TRUE)
Transportation_bymodel
```

### Buildings, Residential

```{r}
Buildings = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 25, "United States", scenario_rename = TRUE)
Buildings
```

### Buildings, Residential by Model

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 31, "United States", scenario_rename = TRUE)
Buildings_bymodel
```

### Buildings, Commercial

```{r}
Buildings = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 26, "United States", scenario_rename = TRUE)
Buildings
```

### Buildings, Commercial by Model

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 32, "United States", scenario_rename = TRUE)
Buildings_bymodel
```
## Percent Electricity

```{r}
Percent_Electricity = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 14, "United States", scenario_rename = TRUE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
Percent_Electricity
```

# Energy Production

## Secondary Energy {.tabset}

### Fuel

```{r}
Fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 15, "United States", scenario_rename = TRUE)
Fuel
```

### Model

```{r, fig.width=12}
Model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 8, "United States", scenario_rename = TRUE)
Model
```

### Model - Zoom

```{r}
Model_zoom = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 25, "United States", scenario_rename = TRUE)
Model_zoom

```

## Electricity Production {.tabset}

### Generation

```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 13, "United States", scenario_rename = TRUE)
elec_gen
```

### Generation by Model

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 15, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
elec_model

```

### Generation by Model - Zoom

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 27, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
elec_model

```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,13)
figure_subset_vars <- unique(figure_subset_df$variable)
se_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, figure_subset_vars, data_long_clean, config)
se_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity", data_long_clean, config)


se_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Coal", data_long_clean, config)
se_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Gas", data_long_clean, config)
se_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Oil", data_long_clean, config)
se_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Solar", data_long_clean, config)
se_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Wind", data_long_clean, config)


```


### Capacity

```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 3, "United States", scenario_rename = TRUE)
Capacity
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,3)
figure_subset_vars <- unique(figure_subset_df$variable)
cap_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, figure_subset_vars, data_long_clean, config)

cap_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Coal", data_long_clean, config)
cap_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Gas", data_long_clean, config)
cap_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Oil", data_long_clean, config)
cap_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Solar", data_long_clean, config)
cap_storage_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Storage Capacity", data_long_clean, config)
cap_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Wind", data_long_clean, config)
```

Electricity capacity is estimated to increase from 2020 to 2040:

-   GCAM: `r cap_value_list[1]`%
-   OP-NEMS: `r cap_value_list[2]`%
-   USREP-ReEDS: `r cap_value_list[3]`%

By technology, electricity capacity is estimated to change from 2020 to 2040:

-   Coal:
    -   GCAM: `r cap_coal_value_list[1]`%
    -   OP-NEMS: `r cap_coal_value_list[2]`%
    -   USREP-ReEDS: `r cap_coal_value_list[3]`%
-   Gas:
    -   GCAM: `r cap_gas_value_list[1]`%
    -   OP-NEMS: `r cap_gas_value_list[2]`%
    -   USREP-ReEDS: `r cap_gas_value_list[3]`%
-   Oil:
    -   GCAM: `r cap_oil_value_list[1]`%
    -   OP-NEMS: `r cap_oil_value_list[2]`%
-   Solar:
    -   GCAM: `r cap_solar_value_list[1]`%
    -   OP-NEMS: `r cap_solar_value_list[2]`%
    -   USREP-ReEDS: `r cap_solar_value_list[3]`%
-   Storage:
    -   OP-NEMS: `r cap_storage_value_list[1]`%
    -   USREP-ReEDS: `r cap_storage_value_list[2]`%
-   Wind:
    -   GCAM: `r cap_wind_value_list[1]`%
    -   OP-NEMS: `r cap_wind_value_list[2]`%
    -   USREP-ReEDS: `r cap_wind_value_list[3]`%

### Capacity by Model

```{r, fig.width=12}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 16, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
elec_model

```

### Capacity by Model - Zoom

```{r}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 26, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
elec_model

```

## Electricity Production - Combustion {.tabset}

### Generation

```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 6, "United States", scenario_rename = TRUE)
elec_gen
```

### Generation by Model

```{r, fig.width=12}
gen_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 20, "United States", scenario_rename = TRUE)
gen_by_model
```

### Generation by Model - Zoom

```{r}
gen_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 28, "United States", scenario_rename = TRUE)
gen_by_model
```

### Capacity

```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 4, "United States", scenario_rename = TRUE)
Capacity
```

### Capacity by Model

```{r, fig.width=12}
cap_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 22, "United States", scenario_rename = TRUE)
cap_by_model
```

### Capacity by Model - Zoom

```{r}
cap_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 29, "United States", scenario_rename = TRUE)
cap_by_model
```

## Electricity Production - Non-Combustion {.tabset}

### Generation

```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 7, "United States", scenario_rename = TRUE)
elec_gen
```

### Generation by Model

```{r}
gen_by_model_nc = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 23, "United States", scenario_rename = TRUE)
gen_by_model_nc
```

### Capacity

```{r}
Capacity_nc = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 5, "United States", scenario_rename = TRUE)
Capacity_nc
```

### Capacity by Model

```{r}
cap_by_model_nc = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 21, "United States", scenario_rename = TRUE)
cap_by_model_nc
```


------------------------------------------------------------------------

# Model Comparision

## Reference Model: {.tabset}

### GCAM

```{r}
diff_from_gcam = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 23, "United States", scenario_rename = TRUE)
diff_from_gcam
```

### OP-NEMS

```{r}
diff_from_nems = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 25, "United States", scenario_rename = TRUE)
diff_from_nems
```

### USREP-ReEDS

```{r}
diff_from_usrep = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 24, "United States", scenario_rename = TRUE)
diff_from_usrep
```

## Input Assumptions {.tabset}

### Population

```{r}
pop = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 12, "United States", scenario_rename = TRUE)
pop
```

### GDP

```{r}
gdp = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 13, "United States", scenario_rename = TRUE)
gdp
```


# Ad-hoc tables/figs

Buildings and electricity emissions table

```{r}
get_value_breakout <- function(data_long_clean, var_list, config) {
data_wm_usa <- data_long_clean %>% filter(scenario == 'wm',
                                             region == 'United States')

var_df <- data_wm_usa %>% filter(variable %in% var_list)

var_df_clean <- var_df %>%
  select(model, year, variable, value) %>%
  filter(year %in% config$fives_sumtab) %>%
  distinct() %>%
  mutate(across(where(is.numeric), round, 1))
return(var_df_clean)
}

var_list <- c('Emissions|CO2|Energy|Demand|Buildings',
              'Emissions|CO2|Energy|Supply|Electricity')

be_df <- get_value_breakout(data_long_clean, var_list, config)
```

Fuel Usage in Buildings Residential vs. Commercial

```{r}
var_list <-  c('Final Energy|Buildings|Residential|Electricity',
               'Final Energy|Buildings|Residential')

br_df <- get_value_breakout(data_long_clean, var_list, config)

```

```{r}
var_list <-  c('Final Energy|Buildings|Commercial|Electricity',
               'Final Energy|Buildings|Commercial')

bc_df <- get_value_breakout(data_long_clean, var_list, config)

```

Electricity generation breakout

```{r}
df <- figmap_nrgco2_stackbar %>% filter(figure_no == 13)

var_list <- df$variable

eg_df <- get_value_breakout(data_long_clean, var_list, config)
```

```{r}
var_list <- c('Secondary Energy|Electricity|Wind','Secondary Energy|Electricity|Solar','Secondary Energy|Electricity')
sw_df <- get_value_breakout(data_long_clean, var_list, config)
```

Primary Energy Coal
```{r}
var_list <- 'Primary Energy|Coal'

pec_df <- get_value_breakout(data_long_clean,var_list, config)
```

Vehicle sales
```{r}
var_list <- "Energy Service|Transportation|EV|Sales Share"

vs_df <- get_value_breakout(data_long_clean,var_list, config)
```

