---
title: "BTR Results Overview W/ Sensitivities"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
source('packages.R')
source("scripts/theming.R")
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_sens_timeseries
    )
  )
```

# Energy CO2 Emissions

## Sector {.tabset}

### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))

df <- data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 9, "United States")
```

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 42, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
```


### Supply-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 10, "United States")
```


### Buildings-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 41, "United States")
```

## Fuel {.tabset}

### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 30, "United States")
```

## CCS {.tabset}

### Topline


```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 39, "United States", scenario_rename = TRUE)
```

### Supply & Demand

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 40, "United States", scenario_rename = TRUE)
```

# Demand

## Final Energy

### Fuel {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 1, "United States", scenario_rename = TRUE)
```

#### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 24, "United States", scenario_rename = TRUE)
```


### Sector {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 2, "United States", scenario_rename = TRUE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
```


## Sectoral Detail

### Buildings {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 17, "United States", scenario_rename = TRUE,
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy"))
```


#### Residential by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 31, "United States", scenario_rename = TRUE)
```


#### Commercial by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 32, "United States", scenario_rename = TRUE)
```


### Industry {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 18, "United States", scenario_rename = TRUE)
```

### Transportation {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 19, "United States", scenario_rename = TRUE)
```


### Vehicle Share {.tabset}

#### Sales Share 

```{r}
df1 = data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 33, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Freight")
df2 = data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 34, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Passenger")
df = rbind(df1,df2)

var_palette <- unique(df$model)

ggplot(data = df) +
  geom_line(aes(x=year,y=value, colour = model), size = 1) +
  facet_grid(facet~variable_rename) +
  scale_color_manual(values = c("GCAM" = "#bfef45",
                                'OP-NEMS' = "#000075",
                                'USREP-ReEDS' = "#9a6324")) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent)  +
  labs(title = 'Vehicle Sales Share') +
  theme(
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1),
        panel.spacing.x = unit(4, "mm"))

```

#### Stock Share 

```{r}
df1 = data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 35, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Freight")
df2 = data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 36, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Passenger")
df = rbind(df1,df2)

ggplot(data = df) +
  geom_line(aes(x=year,y=value, colour = model), size = 1) +
  facet_grid(facet~variable_rename) +
  scale_color_manual(values = c("GCAM" = "#bfef45",
                                'OP-NEMS' = "#000075",
                                'USREP-ReEDS' = "#9a6324")) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent)  +
  labs(title = 'Vehicle Stock Share') +
  theme(
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1),
        panel.spacing.x = unit(4, "mm"))
```

## Percent Electricity

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 14, "United States", scenario_rename = TRUE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
```


# Supply

## Secondary Energy {.tabset}

### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 8, "United States", scenario_rename = TRUE)
```

### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 25, "United States", scenario_rename = TRUE)
```


## Electricity Production 

### Generation {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 15, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
```

#### Model - Zoom

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 27, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
```

### Generation Inputs {.tabset}

#### Totals

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 37, "United States", scenario_rename = TRUE)
```

#### w/ and w/o CCS

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 38, "United States", scenario_rename = TRUE)
```

### Capacity {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 16, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
```

#### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 26, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
```


## Combustion {.tabset}

### Generation by Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 20, "United States", scenario_rename = TRUE)
```

### Generation by Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 28, "United States", scenario_rename = TRUE)
```



### Capacity by Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 22, "United States", scenario_rename = TRUE)
```

### Capacity by Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 29, "United States", scenario_rename = TRUE)
```

## Non-Combustion {.tabset}



### Generation by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 23, "United States", scenario_rename = TRUE)
```



### Capacity by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 21, "United States", scenario_rename = TRUE)
```

## Primary Energy {.tabset}

### Fossil 

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 6, "United States", scenario_rename = TRUE)
```

### Non-Fossil

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 7, "United States", scenario_rename = TRUE)
```

## Input Assumptions {.tabset}

### Population

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 12, "United States", scenario_rename = TRUE)
```

### GDP

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 13, "United States", scenario_rename = TRUE)
```

