---
title: "BTR Results Overview W/ Sensitivities"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
source('packages.R')
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_deck_timeseries
    )
  )

source("scripts/theming.R")

saveit = function(title, settings, width = 10, height = 5) {
  ggsave(filename = paste0("output/",settings$version,"/results_overview_sens_deck/",title,".png"),
         
         create.dir = TRUE,
         width = width,
         height = height,
         units = "in")
}

bottom = theme(legend.position="bottom",legend.direction="vertical")
data_long_clean_100 = data_long_clean %>% mutate(value = value*100)
```

# Emissions {.tabset}

## Gross Emissions
```{r}
title = "Energy Emissions by Sector"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 9.1, "United States",
            level_var = c("Buildings", "Industry", "Transportation", "Electricity", "Petroleum Refining", "Total Energy")) +
  labs(title = "", y = expression(paste("Energy Emissions (Mt C", O[2],")"))) 
saveit(title,settings, width = 13)
```

## CCS
```{r}
title = "Carbon Capture and Storage (CCS)"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States") +
  labs(title="", y = expression(paste("Captured and Stored Emissions (Mt C", O[2],")"))) +
  bottom
saveit(title,settings, width = 6)
```

# Primary/Final Energy {.tabset}

## Primary Energy 
```{r}
fossil = print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 6, "United States") +
  labs(title = "Fossil", y = "Primary Energy (EJ/yr)")

# Check GCAM nuclear units
non_fossil = print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 7, "United States") +
  labs(title = "Non-Fossil", y = "")

title = "Primary Energy"
fossil+non_fossil+plot_layout(guides = "collect", widths = c(1, 2))
saveit(title,settings, width = 15, height = 4)
```

## Final Energy {.tabset}

### Fuel
```{r}
title = "Final Energy by Source"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 1, "United States") +
  labs(title = "", y = "Final Energy (EJ/yr)") 
saveit(title,settings, width = 14)
```

### Percent Electricity
```{r}
title = "Energy Demand Met by Electricity"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 14, "United States",
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity")) +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.y = element_blank()) +
  labs(title = title) +
  bottom
saveit(title,settings, width = 6)
```

### Hydrogen
```{r}
title = "Hydrogen Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 1.1, "United States") +
  labs(title = "", y = "Demand (EJ/yr)") +
  bottom
saveit(title,settings, width = 4)
```

# Electricity

## Load Growth
```{r}
title = "Load Growth"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 15.1, "United States") +
  labs(title = "") +
  bottom
saveit(title,settings,width=4)
```

## Generation by Source
```{r}
title = "Generation"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 15, "United States",
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Generation")) +
  labs(title = "", y = "Electricity Generation (EJ/yr)")
saveit(title,settings,width=15)
```

## Capacity by Source
```{r}
title = "Capacity"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 16, "United States",
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Capacity")) +
  labs(title = "", y = "Electricity Capacity (GW)")
saveit(title,settings,width=15)
```

# Sectoral Energy Demand {.tabset}

## Buildings
```{r}
title = "Buildings Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 17, "United States",
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy")) +
  labs(title = "", y = "Buildings Demand (EJ/yr)") +
  bottom
saveit(title,settings,width=6)
```

## Industry
```{r}
title = "Industry Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 18, "United States",
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy")) +
  labs(title = "", y = "Industry Demand (EJ/yr)") +
  bottom
saveit(title,settings,width=6)
```

## Transportation {.tabset}

### Energy Demand
```{r}
title = "Transportation Demand"
print_graph_for_save("time_series", config, data_long_clean_100, figmap_deck_timeseries, 19, "United States") +
  labs(title = "", y = "Transportation Demand (EJ/yr)") +
  bottom
saveit(title,settings,width=6)
```

### Vehicle Sales and Stock

```{r}
print_graph_for_save("time_series", config, data_long_clean_100, figmap_deck_timeseries, 34, "United States")

print_graph_for_save("time_series", config, data_long_clean_100, figmap_deck_timeseries, 34, "United States")
```




# Stats

```{r}
var_year_comparison <- function(data_from_graph, var_choice, comparison_year) {
 
  var_df <- data_from_graph %>%
    filter(variable == var_choice,
           year == comparison_year) %>%
    group_by(model,scenario,year,variable) %>%
    summarise(value = sum(value))
}


```


## Energy CO2 Emissions

```{r}

df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 9.1, "United States")

```


## CCS Emissions

```{r}

df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States")

ccs_df <- df %>%
  filter(!year %in% c(2045,2050)) %>% 
  group_by(model,scenario) %>%
  summarise(value = sum(value))

```

## Primary Energy Fossil

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 6, "United States")

coal_df <- var_year_comparison(df,"Primary Energy|Coal",2040)

oil_df <- var_year_comparison(df,"Primary Energy|Oil",2040)
  

gas_df <- var_year_comparison(df,"Primary Energy|Gas",2040)

```


## Primary Energy Non-Fossil
```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 7, "United States")

solar_df <- var_year_comparison(df,"Primary Energy|Solar",2040)


wind_df <- var_year_comparison(df,"Primary Energy|Wind",2040)


biomass_df <- df %>%
  filter(year == 2040,
         variable == "Primary Energy|Biomass",
         !model == "USREP-ReEDS") %>% 
  group_by(model,scenario,year,variable) %>%
  summarise(value = sum(value))

nuclear_df <- var_year_comparison(df,"Primary Energy|Nuclear",2040)


```

## Final Energy by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 1, "United States")

feoil_df <- var_year_comparison(df,"Final Energy|Oil",2050)
  

```

## Final Energy by Sector

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 14, "United States")

building_df <- var_year_comparison(df, "Final Energy|Buildings|Percent Electricity", 2040)

transportation_df <- var_year_comparison(df, "Final Energy|Transportation|Percent Electricity", 2040)

industry_df <- var_year_comparison(df, "Final Energy|Industry|Percent Electricity", 2040)

```
## Final Energy H2

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States")


```

## Elec Generation by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 15, "United States")

share_clean_df <- df %>%
  mutate(variable = case_when(variable %in% c("Secondary Energy|Electricity|Solar",
                                              "Secondary Energy|Electricity|Wind") ~ "Secondary Energy|Electricity|Clean",
                              TRUE~variable)) %>%
  group_by(model,scenario,year,variable) %>%
  summarise(value = sum(value)) %>%
  filter(variable %in% c("Secondary Energy|Electricity|Clean",
                         "Secondary Energy|Electricity")) %>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(share_clean = `Secondary Energy|Electricity|Clean` / `Secondary Energy|Electricity`) %>%
  mutate(share_clean = round(share_clean,3)) %>%
  select(model,scenario,year,share_clean)

share_clean_2035 <- share_clean_df %>%
  filter(year == 2035)

share_clean_2040 <- share_clean_df %>%
  filter(year == 2040)
 

solar_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Solar", 2040)

wind_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Wind", 2040)

coal_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Coal", 2050)



```

## Elec Capacity by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 16, "United States")

solar_cap_df <- var_year_comparison(df,"Capacity|Electricity|Solar",2040)

wind_cap_df <- var_year_comparison(df,"Capacity|Electricity|Wind",2040)

coal_cap_df <- var_year_comparison(df,"Capacity|Electricity|Coal",2040)

```

## Energy Demand by Sector

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 17, "United States")

buildings_change <- df %>%
  filter(variable == "Final Energy|Buildings",
         year %in% c(2020,2040)) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value)) %>%
  pivot_wider(names_from = year,
              values_from = value) %>%
  mutate(pct_change  = 1-(`2040`/`2020`)) %>%
  select(!c(`2020`,`2040`))
  
  
  

buildings_elec_share <- df %>%
  filter(variable %in% c("Final Energy|Buildings|Electricity",
                         "Final Energy|Buildings"),
         year == 2040) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value))%>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(elec_share = `Final Energy|Buildings|Electricity`/`Final Energy|Buildings`) %>%
  select(!c(`Final Energy|Buildings|Electricity`,
            `Final Energy|Buildings`))

```


```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 18, "United States")

ind_df <- var_year_comparison(df,"Final Energy|Industry",2050)

ind_elec_share <- df %>%
  filter(variable %in% c("Final Energy|Industry|Electricity",
                         "Final Energy|Industry"),
         year == 2050) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value))%>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(elec_share = `Final Energy|Industry|Electricity`/`Final Energy|Industry`) %>%
  select(!c(`Final Energy|Industry|Electricity`,
            `Final Energy|Industry`))

```


```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 19, "United States")

trn_df <- var_year_comparison(df, "Final Energy|Transportation",2040)

```




