---
title: "BTR Results Overview W/ Sensitivities"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
source('packages.R')
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_deck_timeseries,
    projections_all_sm,
    projections_ghgi,
    past_proj
    )
  )

usproj_categories = read_xlsx("data-raw/crosswalk/crosswalk_usproj_categories.xlsx")

projections_ghgi = filter(projections_ghgi, year <= 2040)

proj_ghgi_nonco2_pre_bind = projections_ghgi %>% filter(gas != "CO2")

proj_ghgi_nonco2 = proj_ghgi_nonco2_pre_bind %>%
  left_join(usproj_categories, by = "usproj_category") %>%
  select(-usproj_category) %>%
  rename(usproj_category = usproj_category_rename)

source("scripts/theming.R")

saveit = function(title, settings, width = 10, height = 5) {
  ggsave(filename = paste0("output/",settings$version,"/results_overview_sens_deck/",title,".svg"),
         
         create.dir = TRUE,
         width = width,
         height = height,
         units = "in")
}

bottom = theme(legend.position="bottom",legend.direction="vertical")
data_long_clean_100 = data_long_clean %>% mutate(value = value*100)
```

# GHG Emissions

## Net GHGs

```{r}
br_project_sens_noNDC(projections_ghgi, config, settings) +
  labs(y = expression(paste("Net GHG Emissions (Mt ", CO[2], "e)", sep = "")))

saveit("Net GHG Emissions",settings,width = 6, height = 4)
```

## Total Gross Emissions

```{r}
brvs_tge <- read_xlsx("data-extra/BR Voluntary Supplement 2023/totalgrossemissions.xlsx")

brvs_tge_clean <- brvs_tge %>%
  pivot_longer(cols = 2:36,
               names_to = 'Year') %>%
  mutate(Report = "2023 BR Voluntary Supplement") %>% 
  select(Report, Year, value)

past_proj_clean <- past_proj %>%
  select(Report, Year, Emissions) %>%
  rename(Value = Emissions) %>%
  filter(Year <= 2035)


tge_btr <- projections_all_sm %>% 
  filter(!gas == 'LULUCF Sink',
         grouping %in% c('wm_sens','ghgi')) %>%
  group_by(proj_name, grouping, year) %>%
  summarise(value = sum(sum),.groups = 'drop')

tge_base <- tge_btr %>%
  filter(year == settings$base_year) %>%
  rename(Report = grouping,
         Year = year) %>% 
  select(names(brvs_tge_clean))

brvs_ribbon <- brvs_tge_clean %>%
  filter(Year > settings$base_year) %>%
  rbind(tge_base) %>%
  group_by(Year) %>% 
  summarise(max = max(value),
            min = min(value)) %>%
  mutate(Report = "2023 BR Voluntary Supplement",
         Year = as.numeric(Year)) %>%
  select(Report, Year, min, max)

tge_all_long <- tge_btr %>%
  mutate(Report = 'btr_2024') %>%
  rename(Year = year,
         Value = value) %>% 
  select(names(past_proj_clean)) %>%
  rbind(past_proj_clean) %>%
  mutate(Year = as.numeric(Year),
         Report = case_when(Report == "btr_2024" ~ "2024 BTR",
                            Report == "car_2014" ~ "2014 CAR",
                            Report == "br_2016" ~ "2016 BR",
                            Report == "br_2021" ~ "2021 BR",
                            Report == "br_2022" ~ "2022 BR"))
#%>%
 # filter(year %in% config$fives_proj_sm)


ncbr_comp_ribbon <- tge_all_long %>% 
  group_by(Report,Year) %>%
  mutate(min = min(Value),
         max = max(Value)) %>%
  select(Report,Year,min,max) %>%
  distinct()

ncbr_comparison_figure_sens(ncbr_comp_ribbon, tge_all_long, settings, config) +
  labs(y = expression(paste("Total Gross GHG Emissions (Mt ", CO[2], "e)", sep = "")))

title = "Total Gross Emissions NCBR Comparison"
saveit(title,settings,width=9, height=7)
```

## Tables

### Gas

```{r gas summary}
gas_df <- create_summary_table('gas','wm_sens', projections_all_sm, config, settings)
gas_table <- create_html_table(gas_df, 'Gas', settings)
gas_table_merged <- create_html_table_merged(gas_df, 'Gas', settings)

gas_table_merged

gtsave(gas_table_merged, paste0('output/',settings$version,"/results_overview_sens_deck/Gas Table.png"))
```

### Sector

```{r sector summary}
sector_df <- create_summary_table('usproj_sector', 'wm_sens', projections_all_sm, config, settings)
sector_table <- create_html_table(sector_df, 'Sector', settings)
sector_table_merged <- create_html_table_merged(sector_df, 'Sector', settings)

gtsave(sector_table_merged, paste0('output/',settings$version,"/results_overview_sens_deck/Sector Table.png"))
```

# Energy CO2 Emissions {.tabset}

## All Energy Emissions
```{r}
nrg_emissions <- projections_all_sm %>%
  filter(usproj_sector %in% c('Energy','Transportation') & gas == "CO2") %>%
  filter(grouping %in% c('ghgi','wm_sens')) %>%
  group_by(proj_name, year, grouping) %>%
  summarise(nrg_trn_co2 = sum(sum)) %>%
  filter(year %in% config$annual_1990_fives) 

ghgi <- nrg_emissions %>%
  filter(year <= settings$base_year,
         year >= 2005)

proj <- nrg_emissions %>%
  group_by(year) %>% 
  filter(year >= settings$base_year)%>%
    summarise(ymax = max(nrg_trn_co2),
              ymin = min(nrg_trn_co2),
              med = median(nrg_trn_co2),
              .groups = 'drop')

nrg_color <- "#2EAD96"

fig <- 
  ggplot() +
  geom_line(ghgi, mapping = aes(x = year, y = nrg_trn_co2, color = proj_name), color = 'black', size = 0.7) +
  geom_ribbon(proj, mapping = aes(x = year,ymax = ymax, ymin = ymin),
              color = nrg_color,
              fill = nrg_color,
              alpha = 0.4 ,
              size = 0.7)+
    labs(x = 'Year',
         y = expression(paste("Energy Emissions (Mt ", CO[2], ")", sep = ""))) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(breaks = c(seq(1990,2020,by=5), 2022, seq(2025,2040,by=5)), expand = c(0,0)) +
    theme_btr() 
fig
title = "Energy CO2 Emissions"
saveit(title,settings,width=6)
```

## Gross Emissions
```{r}
title = "Energy Emissions by Sector"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 9.1, "United States",
            level_var = c("Buildings", "Industry", "Transportation", "Electricity", "Petroleum Refining", "Total Energy")) +
  labs(title = "", y = expression(paste("Energy Emissions (Mt C", O[2],")"))) +
  theme(legend.position = c(0.12, 0.67))
saveit(title,settings, width = 13)
```

## CCS
```{r}
title = "Carbon Capture and Storage (CCS)"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States") +
  labs(title="", y = expression(paste("Captured and Stored Emissions (Mt C ", O[2],")"))) +
  bottom
saveit(title,settings, width = 6, height = 6)
```

# Primary/Final Energy {.tabset}

## Primary Energy 
```{r}
fossil = print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 6, "United States") +
  labs(title = "Fossil", y = "Primary Energy (EJ/yr)")

no_usrr_biomass = data_long_clean %>%
  filter(!(model == "USREP-ReEDS" & variable == "Primary Energy|Biomass")) %>%
  filter(!(model == "GCAM" & variable == "Primary Energy|Nuclear")) %>%
  filter(variable != "Primary Energy|Other")
non_fossil = print_graph_for_save("time_series", config, no_usrr_biomass, figmap_deck_timeseries, 7, "United States") +
  labs(title = "Non-Fossil", y = "")

title = "Primary Energy"
fossil+non_fossil+plot_layout(guides = "collect", widths = c(1, 2))
saveit(title,settings, width = 15, height = 4)
```

## Final Energy {.tabset}

### Fuel
```{r}
title = "Final Energy by Source"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 1, "United States") +
  labs(title = "", y = "Final Energy (EJ/yr)") +
  theme(legend.position = c(0.15, 0.6))
saveit(title,settings, width = 14)
```

### Percent Electricity
```{r}
title = "Energy Demand Met by Electricity"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 14, "United States",
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity")) +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.y = element_blank()) +
  labs(title = title) +
  bottom
saveit(title,settings, width = 6)
```

### Hydrogen
```{r}
title = "Hydrogen Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 1.1, "United States") +
  labs(title = "", y = "Demand (EJ/yr)") +
  bottom
saveit(title,settings, width = 4)
```

# Electricity

## Load Growth
```{r}
title = "Load Growth"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 15.1, "United States") +
  labs(title = "") +
  bottom
saveit(title,settings,width=5)
```

## Generation by Source
```{r}
title = "Generation"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 15, "United States",
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Generation")) +
  labs(title = "", y = "Electricity Generation (EJ/yr)") +
  theme(legend.position = c(0.12, 0.65))
df1 = data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 15, "United States") %>%
  filter(variable_rename == "Coal")
df = data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 15.01, "United States")
saveit(title,settings,width=15)
```

## Capacity by Source
```{r}
title = "Capacity"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 16, "United States",
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Capacity")) +
  labs(title = "", y = "Electricity Capacity (GW)") +
  theme(legend.position = c(0.12, 0.65))
saveit(title,settings,width=15)
```

# Sectoral Energy Demand {.tabset}

## Buildings
```{r}
title = "Buildings Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 17, "United States",
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy")) +
  labs(title = "", y = "Buildings Demand (EJ/yr)") +
  bottom
saveit(title,settings,width=6)
```

## Industry
```{r}
title = "Industry Demand"
print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 18, "United States",
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy")) +
  labs(title = "", y = "Industry Demand (EJ/yr)") +
  bottom
saveit(title,settings,width=6)
```

## Transportation {.tabset}

### Energy Demand
```{r}
title = "Transportation Demand"
print_graph_for_save("time_series", config, data_long_clean_100, figmap_deck_timeseries, 19, "United States") +
  labs(title = "", y = "Transportation Demand (EJ/yr)") 
saveit(title,settings,width=13)
```

### Vehicle Sales and Stock

```{r}
sales = print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 33, "United States",
                             level_var = c("ICE", "BEV", "HEV", "PHEV", "FCEV")) +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.y = element_blank()) +
  labs(title = "Sales Share")

stock = print_graph_for_save("time_series", config, data_long_clean, figmap_deck_timeseries, 34, "United States",
                             level_var = c("ICE", "BEV", "HEV", "PHEV", "FCEV")) +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.y = element_blank()) +
  labs(title = "Stock Share")

title = "Vehicles Sales and Stock Share"
sales+stock+plot_layout(guides = "collect", widths = c(1, 1))
saveit(title,settings, width = 15)
```

# Stats

```{r}
var_year_comparison <- function(data_from_graph, var_choice, comparison_year) {
 
  var_df <- data_from_graph %>%
    filter(variable == var_choice,
           year == comparison_year) %>%
    group_by(model,scenario,year,variable) %>%
    summarise(value = sum(value))
}


```


## Energy CO2 Emissions

```{r}

df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 9.1, "United States")

```


## CCS Emissions

```{r}

df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States")

ccs_df <- df %>%
  filter(!year %in% c(2045,2050)) %>% 
  group_by(model,scenario) %>%
  summarise(value = sum(value))

```

## Primary Energy Fossil

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 6, "United States")

coal_df <- var_year_comparison(df,"Primary Energy|Coal",2040)

oil_df <- var_year_comparison(df,"Primary Energy|Oil",2040)
  

gas_df <- var_year_comparison(df,"Primary Energy|Gas",2040)

```


## Primary Energy Non-Fossil
```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 7, "United States")

solar_df <- var_year_comparison(df,"Primary Energy|Solar",2040)


wind_df <- var_year_comparison(df,"Primary Energy|Wind",2040)


biomass_df <- df %>%
  filter(year == 2040,
         variable == "Primary Energy|Biomass",
         !model == "USREP-ReEDS") %>% 
  group_by(model,scenario,year,variable) %>%
  summarise(value = sum(value))

nuclear_df <- var_year_comparison(df,"Primary Energy|Nuclear",2040)


```

## Final Energy by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 1, "United States")

feoil_df <- var_year_comparison(df,"Final Energy|Oil",2050)
  

```

## Final Energy by Sector

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 14, "United States")

building_df <- var_year_comparison(df, "Final Energy|Buildings|Percent Electricity", 2040)

transportation_df <- var_year_comparison(df, "Final Energy|Transportation|Percent Electricity", 2040)

industry_df <- var_year_comparison(df, "Final Energy|Industry|Percent Electricity", 2040)

```

## Final Energy H2

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 39, "United States")
```

## Elec Generation by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 15.2, "United States")

share_clean_df <- df %>%
  mutate(variable = case_when(variable %in% c("Secondary Energy|Electricity|Solar",
                                              "Secondary Energy|Electricity|Wind") ~ "Secondary Energy|Electricity|Clean",
                              TRUE~variable)) %>%
  group_by(model,scenario,year,variable) %>%
  summarise(value = sum(value)) %>%
  filter(variable %in% c("Secondary Energy|Electricity|Clean",
                         "Secondary Energy|Electricity")) %>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(share_clean = `Secondary Energy|Electricity|Clean` / `Secondary Energy|Electricity`) %>%
  mutate(share_clean = round(share_clean,3)) %>%
  select(model,scenario,year,share_clean)

share_clean_2035 <- share_clean_df %>%
  filter(year == 2035)

share_clean_2040 <- share_clean_df %>%
  filter(year == 2040)
 
solar_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Solar", 2040)
wind_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Wind", 2040)
coal_gen_df <- var_year_comparison(df, "Secondary Energy|Electricity|Coal", 2050)
```

## Elec Capacity by Source

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 16, "United States")

solar_cap_df <- var_year_comparison(df,"Capacity|Electricity|Solar",2040)
wind_cap_df <- var_year_comparison(df,"Capacity|Electricity|Wind",2040)
coal_cap_df <- var_year_comparison(df,"Capacity|Electricity|Coal",2040)
```

## Energy Demand by Sector

```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 17, "United States")

buildings_change <- df %>%
  filter(variable == "Final Energy|Buildings",
         year %in% c(2020,2040)) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value)) %>%
  pivot_wider(names_from = year,
              values_from = value) %>%
  mutate(pct_change  = 1-(`2040`/`2020`)) %>%
  select(!c(`2020`,`2040`))
  
buildings_elec_share <- df %>%
  filter(variable %in% c("Final Energy|Buildings|Electricity",
                         "Final Energy|Buildings"),
         year == 2040) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value))%>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(elec_share = `Final Energy|Buildings|Electricity`/`Final Energy|Buildings`) %>%
  select(!c(`Final Energy|Buildings|Electricity`,
            `Final Energy|Buildings`))
```


```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 18, "United States")

ind_df <- var_year_comparison(df,"Final Energy|Industry",2050)

ind_elec_share <- df %>%
  filter(variable %in% c("Final Energy|Industry|Electricity",
                         "Final Energy|Industry"),
         year == 2050) %>%
  group_by(model, scenario, year, variable) %>%
  summarise(value = sum(value))%>%
  pivot_wider(names_from = variable,
              values_from = value) %>%
  mutate(elec_share = `Final Energy|Industry|Electricity`/`Final Energy|Industry`) %>%
  select(!c(`Final Energy|Industry|Electricity`,
            `Final Energy|Industry`))
```


```{r}
df <- data_from_graph("time_series", config, data_long_clean, figmap_deck_timeseries, 19, "United States")
trn_df <- var_year_comparison(df, "Final Energy|Transportation",2040)
```

# Non-CO2

## Non-CO2 Gas and Sector Matrix
```{r}
all_gases = projections_all_sm %>% 
  filter(grouping == "wm" & gas != "CO2") %>%
  filter(usproj_sector != "LULUCF Sink") %>%
  filter(!(str_detect(proj_name, "usrr") & usproj_sector %in% c("Transportation","Energy") & year %in% c(2045, 2050))) %>%
  filter(!(usproj_sector == "Energy" & !year %in% c(2020, 2025, 2030, 2035, 2040, 2045, 2050))) %>%
  filter(year <= 2040)

ggplot() +
  geom_line(data = all_gases, aes(x=year,y=sum,group=proj_name,color=gas), linewidth = 1) +
  facet_grid(gas~usproj_sector, scales = "free_y") +
  labs(y = "Mt CO2e") +
  theme_btr() +
  theme(
    #text = element_text(size = 20),
        strip.text.x = element_text(size = 14),
        strip.text.y = element_text(size = 14),
        text = element_text(size = 14)) +
  nolegend  +
  scale_color_brewer(palette = "Paired")
saveit("Non-CO2 Gas Sector Matrix",settings, height = 8)
```

## Agriculture
```{r}
tge_breakout_figure_sm(proj_ghgi_nonco2, sector_select = 'Agriculture')  +
  labs(title = "")
saveit("Agriculture Non-CO2",settings, width = 8)
```

## Energy
```{r}
tge_breakout_figure_sm(proj_ghgi_nonco2, sector_select = 'Energy', col_count = 4)  +
  labs(title = "")
saveit("Energy Non-CO2",settings, width = 15)
```

## IPPU
```{r}
# IPPU Non-Energy CO2
tge_breakout_figure_sm(filter(projections_ghgi, gas == "CO2"), sector_select = 'IPPU')  +
  labs(title = "IPPU: Non-Energy CO2")
# IPPU Non-CO2
tge_breakout_figure_sm(proj_ghgi_nonco2, sector_select = 'IPPU', col_count = 4)  +
  labs(title = "")
# filtering out miniscule categories
proj_ghgi_nonco2_sm = proj_ghgi_nonco2 %>%
  filter(!usproj_category %in% c(
    "Iron Steel Metallurgical Coke",
    "Carbide Production",
    "Ferroalloy Production",
    "N2O Product Use",
    "Petrochemicals"))
tge_breakout_figure_sm(proj_ghgi_nonco2_sm, sector_select = 'IPPU', col_count = 6)  +
  labs(title = "")
saveit("IPPU Non-CO2",settings, width = 17)
```

## Transportation
```{r}
tge_breakout_figure_sm(proj_ghgi_nonco2, sector_select = 'Transportation') + 
  labs(title = "")
saveit("Transportation Non-CO2",settings, width = 8)
```

## Waste
```{r}
no_standalone_digesters = proj_ghgi_nonco2 %>%
  filter(usproj_category != "StandaloneDigesters")
tge_breakout_figure_sm(no_standalone_digesters, sector_select = 'Waste', col_count = 4)  +
  labs(title = "")
saveit("Waste Non-CO2",settings, width = 11, height = 4)
```

```{r}
projections_ghgi %>%
  select(usproj_category) %>%
  distinct(usproj_category) %>%
  write_csv("categories.csv")
```