---
title: "BTR Results Overview"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r Sys.time()`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```


```{r}
library(targets)
library(tarchetypes)
tar_source()
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm,
    figmap_nrgco2_stackbar,
    figmap_nrgco2_timeseries,
    figmap_nrgco2_diffbar
    )
  )
```

```{r}
source('packages.R')
source("scripts/theming.R")
```



# Emissions

## Energy CO2 Emissions {.tabset}

### Sector

```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 19, "United States", scenario_rename = TRUE)
sector
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,19)
figure_subset_vars <- unique(figure_subset_df$variable)
nrgco2_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, figure_subset_vars, data_long_clean, config)

buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Buildings", data_long_clean, config)
industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Industry", data_long_clean, config)
transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Transportation", data_long_clean, config)


```


In the "With Measures" scenarios, Energy CO~2~ emissions reductions range by model from 2020 to 2040:

* GCAM: `r nrgco2_value_list[1]`%
* OP-NEMS: `r nrgco2_value_list[2]`%
* USREP-ReEDS: `r nrgco2_value_list[3]`%



### Model

```{r}
model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
model
```




By sector, emissions reductions are estimate to change from 2020 to 2040:

* Buildings:
  + GCAM: `r buildings_value_list[1]`%
  + OP-NEMS: `r buildings_value_list[2]`%
  + USREP-ReEDS: `r buildings_value_list[3]`%

* Industry:
  + GCAM: `r industry_value_list[1]`%
  + OP-NEMS: `r industry_value_list[2]`%
  + USREP-ReEDS: `r industry_value_list[3]`%

* Transportation:
  + GCAM: `r transportation_value_list[1]`%
  + OP-NEMS: `r transportation_value_list[2]`%
  + USREP-ReEDS: `r transportation_value_list[3]`%

# Energy Consumption

## Final Energy {.tabset}

### Fuel
```{r}
fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 14, "United States", scenario_rename = TRUE)
fuel
```

### Fuel by Model
```{r}
Fuel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 1, "United States", scenario_rename = TRUE)
Fuel
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,14)
figure_subset_vars <- unique(figure_subset_df$variable)
final_energy_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, figure_subset_vars, data_long_clean, config)

fe_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Final Energy|Coal", data_long_clean, config)
fe_electricity_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Final Energy|Electricity", data_long_clean, config)
fe_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Final Energy|Gas", data_long_clean, config)
fe_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Final Energy|Oil", data_long_clean, config)

```

Energy consumption is estimated to change from 2020 to 2040:

* GCAM: `r final_energy_value_list[1]`%
* OP-NEMS: `r final_energy_value_list[2]`%
* USREP-ReEDS: `r final_energy_value_list[3]`%

By fuel-type, energy consumption is estimated to change from 2020 to 2040:

* Coal:
  + GCAM: `r fe_coal_value_list[1]`%
  + OP-NEMS: `r fe_coal_value_list[2]`%
  + USREP-ReEDS: `r fe_coal_value_list[3]`%

* Electricity:
  + GCAM: `r fe_electricity_value_list[1]`%
  + OP-NEMS: `r fe_electricity_value_list[2]`%
  + USREP-ReEDS: `r fe_electricity_value_list[3]`%

* Gas:
  + GCAM: `r fe_gas_value_list[1]`%
  + OP-NEMS: `r fe_gas_value_list[2]`%
  + USREP-ReEDS: `r fe_gas_value_list[3]`%
  
* Oil:
  + GCAM: `r fe_oil_value_list[1]`%
  + OP-NEMS: `r fe_oil_value_list[2]`%
  + USREP-ReEDS: `r fe_oil_value_list[3]`%

### Sector
```{r}
sector = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 17, "United States", scenario_rename = TRUE)
sector
```

```{r}
fe_buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Buildings", data_long_clean, config)
fe_industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Industry", data_long_clean, config)
fe_transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Transportation", data_long_clean, config)

```

By sector, energy consumption is estimated to change from 2020 to 2040:

* Buildings:
  + GCAM: `r fe_buildings_value_list[1]`%
  + OP-NEMS: `r fe_buildings_value_list[2]`%
  + USREP-ReEDS: `r fe_buildings_value_list[3]`%

* Industry:
  + GCAM: `r fe_industry_value_list[1]`%
  + OP-NEMS: `r fe_industry_value_list[2]`%
  + USREP-ReEDS: `r fe_industry_value_list[3]`%

* Transportation:
  + GCAM: `r fe_transportation_value_list[1]`%
  + OP-NEMS: `r fe_transportation_value_list[2]`%
  + USREP-ReEDS: `r fe_transportation_value_list[3]`%


### Sector by Model
```{r}
Sector = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 2, "United States", scenario_rename = TRUE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
Sector
```




## Final Energy by Sector {.tabset}

### Buildings
```{r}
Buildings = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 8, "United States", scenario_rename = TRUE)
Buildings
```

### Buildings by Model

```{r}
Buildings_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 17, "United States", scenario_rename = TRUE)
Buildings_bymodel
```

### Industry
```{r}
Industry = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 9, "United States", scenario_rename = TRUE)
Industry
```

### Industry by Model

```{r}
Industry_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 18, "United States", scenario_rename = TRUE)
Industry_bymodel
```

### Transportation
```{r}
Transportation = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 12, "United States", scenario_rename = TRUE)
Transportation
```

### Transportation by Model

```{r}
Transportation_bymodel = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 19, "United States", scenario_rename = TRUE)
Transportation_bymodel
```

## Percent Electricity

```{r}
Percent_Electricity = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 14, "United States", scenario_rename = TRUE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
Percent_Electricity
```

# Energy Production

## Secondary Energy {.tabset}

### Fuel
```{r}
Fuel = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 15, "United States", scenario_rename = TRUE)
Fuel
```

### Model
```{r}
Model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 8, "United States", scenario_rename = TRUE)
Model
```

## Electricity Production {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 13, "United States", scenario_rename = TRUE)
elec_gen
```

### Generation by Model

```{r}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 15, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
elec_model

```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,13)
figure_subset_vars <- unique(figure_subset_df$variable)
se_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, figure_subset_vars, data_long_clean, config)

se_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Coal", data_long_clean, config)
se_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Gas", data_long_clean, config)
se_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Oil", data_long_clean, config)
se_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Solar", data_long_clean, config)
se_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Wind", data_long_clean, config)


```

Electricity generation is estimated to increase from 2020 to 2040:

* GCAM: `r se_value_list[1]`%
* OP-NEMS: `r se_value_list[2]`%
* USREP-ReEDS: `r se_value_list[3]`%

By technology, electricity generation is estimated to change from 2020 to 2040:

* Coal:
  + GCAM: `r se_coal_value_list[1]`%
  + OP-NEMS: `r se_coal_value_list[2]`%
  + USREP-ReEDS: `r se_coal_value_list[3]`%

* Gas:
  + GCAM: `r se_gas_value_list[1]`%
  + OP-NEMS: `r se_gas_value_list[2]`%
  + USREP-ReEDS: `r se_gas_value_list[3]`%
  
* Oil:
  + GCAM: `r se_oil_value_list[1]`%
  + OP-NEMS: `r se_oil_value_list[2]`%

* Solar:
  + GCAM: `r se_solar_value_list[1]`%
  + OP-NEMS: `r se_solar_value_list[2]`%
  + USREP-ReEDS: `r se_solar_value_list[3]`%
  
* Wind:
  + GCAM: `r se_wind_value_list[1]`%
  + OP-NEMS: `r se_wind_value_list[2]`%
  + USREP-ReEDS: `r se_wind_value_list[3]`%
  

### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 3, "United States", scenario_rename = TRUE)
Capacity
```

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,3)
figure_subset_vars <- unique(figure_subset_df$variable)
cap_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, figure_subset_vars, data_long_clean, config)

cap_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Coal", data_long_clean, config)
cap_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Gas", data_long_clean, config)
cap_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Oil", data_long_clean, config)
cap_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Solar", data_long_clean, config)
cap_storage_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Storage Capacity", data_long_clean, config)
cap_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Wind", data_long_clean, config)


```


Electricity capacity is estimated to increase from 2020 to 2040:

* GCAM: `r cap_value_list[1]`%
* OP-NEMS: `r cap_value_list[2]`%
* USREP-ReEDS: `r cap_value_list[3]`%

By technology, electricity capacity is estimated to change from 2020 to 2040:

* Coal:
  + GCAM: `r cap_coal_value_list[1]`%
  + OP-NEMS: `r cap_coal_value_list[2]`%
  + USREP-ReEDS: `r cap_coal_value_list[3]`%

* Gas:
  + GCAM: `r cap_gas_value_list[1]`%
  + OP-NEMS: `r cap_gas_value_list[2]`%
  + USREP-ReEDS: `r cap_gas_value_list[3]`%
  
* Oil:
  + GCAM: `r cap_oil_value_list[1]`%
  + OP-NEMS: `r cap_oil_value_list[2]`%

* Solar:
  + GCAM: `r cap_solar_value_list[1]`%
  + OP-NEMS: `r cap_solar_value_list[2]`%
  + USREP-ReEDS: `r cap_solar_value_list[3]`%

* Storage:
  + OP-NEMS: `r cap_storage_value_list[1]`%
  + USREP-ReEDS: `r cap_storage_value_list[2]`%
  
* Wind:
  + GCAM: `r cap_wind_value_list[1]`%
  + OP-NEMS: `r cap_wind_value_list[2]`%
  + USREP-ReEDS: `r cap_wind_value_list[3]`%



### Capacity by Model

```{r}
elec_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 16, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
elec_model

```

## Electricity Production - Combustion {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 6, "United States", scenario_rename = TRUE)
elec_gen
```

### Generation by Model

```{r}
gen_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 20, "United States", scenario_rename = TRUE)
gen_by_model
```

### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 4, "United States", scenario_rename = TRUE)
Capacity
```

### Capacity by Model

```{r}
cap_by_model = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 21, "United States", scenario_rename = TRUE)
cap_by_model
```

## Electricity Production - Non-Combustion {.tabset}

### Generation
```{r}
elec_gen = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 7, "United States", scenario_rename = TRUE)
elec_gen
```


### Capacity
```{r}
Capacity = print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 5, "United States", scenario_rename = TRUE)
Capacity
```

---
# Model Comparision 

## Reference Model: {.tabset}

### GCAM

```{r}
diff_from_gcam = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 23, "United States", scenario_rename = TRUE)
diff_from_gcam
```

### OP-NEMS

```{r}
diff_from_nems = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 25, "United States", scenario_rename = TRUE)
diff_from_nems
```

### USREP-ReEDS

```{r}
diff_from_usrep = print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 24, "United States", scenario_rename = TRUE)
diff_from_usrep
```

## Input Assumptions {.tabset}

### Population
```{r}
pop = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 12, "United States", scenario_rename = TRUE)
pop
```

### GDP
```{r}
gdp = print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 13, "United States", scenario_rename = TRUE)
gdp
```

# BTR Tables and Figures

## Value Summary Tables {.tabset}

```{r create df}
gas_df <- create_summary_table('gas','wm', projections_all_sm, config)
sector_df <- create_summary_table('usproj_sector', 'wm', projections_all_sm, config)
```

### Gas
```{r gas summary}
gas_table <- create_html_table(gas_df, 'Gas',config)

gas_table_merged <- create_html_table_merged(gas_df, 'Gas', config)
gas_table_merged
```


```{r}
filename <- paste0("gas_table_",Sys.Date(),".png")
gtsave(gas_table, paste0('output/',settings$version,"/tables_figs/results_tables/estimated_values/",filename))

```

### Sector
```{r sector summary}
sector_table <- create_html_table(sector_df, 'Sector',config)

sector_table_merged <- create_html_table_merged(sector_df, 'Sector', config)
sector_table_merged
```

```{r}

filename <- paste0("sector_table_",Sys.Date(),".png")
gtsave(sector_table, paste0('output/',settings$version,"/tables_figs/results_tables/estimated_values/",filename))
```

## 2005 Percent Change Table {.tabset}

### Gas
```{r, pct change by gas}
pct_change_table_gas <- create_pct_change_table('gas', 'wm', projections_all_sm, config)
pct_change_html_gas <- create_pct_change_html_table(pct_change_table_gas, 'Gas', config)
pct_change_html_gas
```


```{r}

filename <- paste0("gas_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_gas, paste0('output/',settings$version,"/tables_figs/results_tables/percent_change_2005/",filename))
```

### Sector
```{r, pct change by sector}
pct_change_table_sector <- create_pct_change_table('usproj_sector', 'wm', projections_all_sm, config)
pct_change_html_sector <- create_pct_change_html_table(pct_change_table_sector, 'Sector', config)
pct_change_html_sector
```


```{r}

filename <- paste0("sector_table_pctchange05_",Sys.Date(),".png")
gtsave(pct_change_html_sector, paste0('output/',settings$version,"/tables_figs/results_tables/percent_change_2005/",filename))
```

## BTR Main Plot {.tabset}

```{r data}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum)) %>%
  filter(year %in% config$fives)

ghgi = net_ghg %>% filter(proj_name == "ghgi")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == 2022,]$sum
baseline = ghgi[ghgi$year == 2005,]$sum

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = 2022,
    sum = ghgi$sum[ghgi$year == 2022])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c((baseline * (1-.169)), (baseline * (1-.26)), (baseline * (1-.50))),
  ymax = c((baseline * (1-.171)), (baseline * (1-.28)), (baseline * (1-.52))),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)
```

### Net GHG Emissions
```{r proj function}
projections = br_project(ghgi, proj, config, targets = ndc_targets)
projections

```

```{r}
filename <- paste0("btr_main_fig_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/btr_main_fig/",filename))
```


```{r}
net_ghg = projections_all_sm %>%
  group_by(proj_name, grouping, year) %>%
  summarise(sum = sum(sum),.groups = 'drop') %>%
  filter(year %in% config$fives) %>%
  mutate(pct_change_05 = round((sum/sum[year==2005]-1),2))


ghgi = net_ghg %>% filter(proj_name == "ghgi")
proj_no_connect = net_ghg %>% 
  filter(proj_name != "ghgi")

connect = ghgi[ghgi$year == 2022,]$pct_change_05
baseline = ghgi[ghgi$year == 2005,]$pct_change_05

proj_connect = proj_no_connect %>% 
  group_by(proj_name) %>%
  slice(1) %>%
  mutate(
    year = 2022,
    pct_change_05 = ghgi$pct_change_05[ghgi$year == 2022])

proj = rbind(proj_no_connect, proj_connect) %>%
  mutate(year = as.numeric(year))

ndc_targets = data.frame(
  year = c(2020, 2025, 2030),
  ymin = c(-.17, -.28, -.52),
  ymax = c(-.17, -.26, -.5),
  grouping = c("17% Below 2005","26-28% Below 2005","50-52% Below 2005")
)




```

### Percent Change from 2005

```{r}
projections_pct_change = br_project_pct_change(ghgi, proj, targets = ndc_targets)
projections_pct_change
```

```{r}
filename <- paste0("btr_main_fig_pctchange05_",Sys.Date(),".png")
ggsave(paste0('output/',settings$version,"/tables_figs/btr_main_fig/",filename))
```


## BTR Net-GHG Stackbar

```{r net-ghg stackbar}
net_ghg_sb_df <- net_ghg_sb_data_processing(projections_all_sm, config)

net_ghg_stackbar <- br_project_net_ghg_sb(net_ghg_sb_df, config)

net_ghg_stackbar
```

