---
title: "BTR Results Overview W/ Sensitivities"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
source('packages.R')
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_sens_timeseries
    )
  )

source("scripts/theming.R")

```

# Energy CO2 Emissions

## Sector {.tabset}

### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))

df <- data_from_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 9, "United States")
```


### Supply-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 10, "United States")
```


### Buildings-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 41, "United States")
```

### Transportation-Breakout

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 45, "United States")
```

## Fuel

```{r}
# KEEP
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 30, "United States", scenario_rename = TRUE)
```

```{r}
# With Measures
# Advanced Technologies
# Low Fuel Cost
# High Fuel Cost
# High Fuel Cost & Low Cost Renewables
```

## CCS {.tabset}

### Topline


```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 39, "United States", scenario_rename = TRUE)
```

### Supply & Demand

```{r}
# Add facet Biomass vs Fossil, two rows for source
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 40, "United States", scenario_rename = TRUE)
```

# Demand

## Final Energy

### Fuel {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 1, "United States", scenario_rename = TRUE)
```

#### Model - Zoom

```{r}
# Include all scenarios
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 24, "United States", scenario_rename = TRUE)
```


### Sector {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 2, "United States", scenario_rename = TRUE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
```


## Sectoral Detail

### Buildings {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 17, "United States", scenario_rename = TRUE,
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy"))
```


#### Residential by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 31, "United States", scenario_rename = TRUE)
```


#### Commercial by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 32, "United States", scenario_rename = TRUE)
```


### Industry {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 18, "United States", scenario_rename = TRUE)
```

### Transportation {.tabset}

#### Model

```{r}
# Add bio
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 19, "United States", scenario_rename = TRUE)
```

#### Sales Share {.tabset}

##### Passenger 

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 34, "United States", scenario_rename = TRUE)
```

##### Freight

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 33, "United States", scenario_rename = TRUE)
```

#### Stock Share {.tabset}

##### Passenger 

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 36, "United States", scenario_rename = TRUE)
```

##### Freight

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 35, "United States", scenario_rename = TRUE)
```

## Percent Electricity

```{r}
# Change y-axis labels to percents
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 14, "United States", scenario_rename = TRUE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
```


# Supply

## Secondary Energy {.tabset}

### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 8, "United States", scenario_rename = TRUE)
```


## Electricity Production 

### Generation {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 15, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
```

### Generation Inputs {.tabset}

#### Totals

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 37, "United States", scenario_rename = TRUE)
```

#### w/ and w/o CCS

```{r}
# Facet CCS vs No CCS, two rows columns for each tech
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 38, "United States", scenario_rename = TRUE)
```

### Capacity {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 16, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
```


## Combustion {.tabset}

### Generation by Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 20, "United States", scenario_rename = TRUE)
```

### Capacity by Model

```{r, fig.width=12}
# Facet CCS vs. Non-CCS
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 22, "United States", scenario_rename = TRUE)
```


## Non-Combustion {.tabset}



### Generation by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 23, "United States", scenario_rename = TRUE)
```



### Capacity by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 21, "United States", scenario_rename = TRUE)
```

## Primary Energy {.tabset}

### Fossil 

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 6, "United States", scenario_rename = TRUE)
```

### Non-Fossil

```{r}
# Check GCAM nuclear units
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 7, "United States", scenario_rename = TRUE)
```

## Input Assumptions {.tabset}

### Population

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 12, "United States", scenario_rename = TRUE)
```

### GDP

```{r}
print_graph("time_series", config, data_long_clean, figmap_sens_timeseries, 13, "United States", scenario_rename = TRUE)
```

