---
title: "BTR Results Overview"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, 
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

```{r}
library(targets)
library(tarchetypes)
tar_source()
source('packages.R')
source("scripts/theming.R")
```

```{r}
tar_load(
  c(
    config,
    settings,
    data_long_clean,
    projections_all_sm, 
    figmap_nrgco2_stackbar,
    figmap_nrgco2_timeseries,
    figmap_nrgco2_diffbar
    )
  )
```

# Energy CO2 Emissions

## Sector {.tabset}

### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 9, "United States", scenario_rename = TRUE,
            level_var = c("Buildings", "Industry", "Transportation", "Supply", "Total Energy"))
```

### Sector

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 19, "United States", scenario_rename = TRUE)
```

### Supply-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 10, "United States")
```


### Buildings-Breakout
```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 41, "United States")
```


### Stats

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,19)
figure_subset_vars <- unique(figure_subset_df$variable)
nrgco2_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, figure_subset_vars, data_long_clean, config)

buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Buildings", data_long_clean, config)
industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Industry", data_long_clean, config)
transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 19, "Emissions|CO2|Energy|Demand|Transportation", data_long_clean, config)
```

In the "With Measures" scenarios, Energy CO~2~ emissions reductions range by model from 2020 to 2040:

-   GCAM: `r nrgco2_value_list$GCAM`%
-   OP-NEMS: `r nrgco2_value_list$"OP-NEMS"`%
-   USREP-ReEDS: `r nrgco2_value_list$"USREP-ReEDS"`%

By sector, emissions reductions are estimate to change from 2020 to 2040:

-   Buildings:
    -   GCAM: `r buildings_value_list$GCAM`%
    -   OP-NEMS: `r buildings_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r buildings_value_list$"USREP-ReEDS"`%
-   Industry:
    -   GCAM: `r industry_value_list$GCAM`%
    -   OP-NEMS: `r industry_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r industry_value_list$"USREP-ReEDS"`%
-   Transportation:
    -   GCAM: `r transportation_value_list$GCAM`%
    -   OP-NEMS: `r transportation_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r transportation_value_list$"USREP-ReEDS"`%

## Fuel {.tabset}

### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 30, "United States")
```

### Fuel

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 24, "United States", scenario_rename = TRUE)
```

### Stats 

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,24)
figure_subset_vars <- unique(figure_subset_df$variable)
nrgco2_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, figure_subset_vars, data_long_clean, config)

buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Coal", data_long_clean, config)
industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Gas", data_long_clean, config)
transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 24, "Emissions|CO2|Energy|Oil", data_long_clean, config)
```

## CCS {.tabset}

### Topline


```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 39, "United States", scenario_rename = TRUE)
```

### Supply & Demand

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 40, "United States", scenario_rename = TRUE)
```

# Demand

## Final Energy

### Fuel {.tabset}

#### Fuel

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 14, "United States", scenario_rename = TRUE)
```

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 1, "United States", scenario_rename = TRUE)
```

#### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 24, "United States", scenario_rename = TRUE)
```

#### Stats 

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,14)
figure_subset_vars <- unique(figure_subset_df$variable)
final_energy_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, figure_subset_vars, data_long_clean, config)

fe_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Coal", data_long_clean, config)
fe_electricity_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Electricity", data_long_clean, config)
fe_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Gas", data_long_clean, config)
fe_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 14, "Final Energy|Oil", data_long_clean, config)
```

Energy consumption is estimated to change from 2020 to 2040:

-   GCAM: `r final_energy_value_list$GCAM`%
-   OP-NEMS: `r final_energy_value_list$"OP-NEMS"`%
-   USREP-ReEDS: `r final_energy_value_list$"USREP-ReEDS"`%

By fuel-type, energy consumption is estimated to change from 2020 to 2040:

-   Coal:
    -   GCAM: `r fe_coal_value_list$GCAM`%
    -   OP-NEMS: `r fe_coal_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_coal_value_list$"USREP-ReEDS"`%
-   Electricity:
    -   GCAM: `r fe_electricity_value_list$GCAM`%
    -   OP-NEMS: `r fe_electricity_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_electricity_value_list$"USREP-ReEDS"`%
-   Gas:
    -   GCAM: `r fe_gas_value_list$GCAM`%
    -   OP-NEMS: `r fe_gas_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_gas_value_list$"USREP-ReEDS"`%
-   Oil:
    -   GCAM: `r fe_oil_value_list$GCAM`%
    -   OP-NEMS: `r fe_oil_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_oil_value_list$"USREP-ReEDS"`%

### Sector {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 2, "United States", scenario_rename = TRUE,
                     level_var = c("Buildings", "Industry", "Transportation", "Total Energy"))
```

#### Sector

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 17, "United States", scenario_rename = TRUE)
```

#### Stats

```{r}
fe_buildings_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Buildings", data_long_clean, config)
fe_industry_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Industry", data_long_clean, config)
fe_transportation_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 17, "Final Energy|Transportation", data_long_clean, config)
```

By sector, energy consumption is estimated to change from 2020 to 2040:

-   Buildings:
    -   GCAM: `r fe_buildings_value_list$GCAM`%
    -   OP-NEMS: `r fe_buildings_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_buildings_value_list$"USREP-ReEDS"`%
-   Industry:
    -   GCAM: `r fe_industry_value_list$GCAM`%
    -   OP-NEMS: `r fe_industry_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_industry_value_list$"USREP-ReEDS"`%
-   Transportation:
    -   GCAM: `r fe_transportation_value_list$GCAM`%
    -   OP-NEMS: `r fe_transportation_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r fe_transportation_value_list$"USREP-ReEDS"`%

## Sectoral Detail

### Buildings {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 17, "United States", scenario_rename = TRUE,
                                level_var = c("Coal", "Gas", "Oil", 'Electricity',"Total Energy"))
```

#### Buildings

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 8, "United States", scenario_rename = TRUE)
```

#### Residential by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 31, "United States", scenario_rename = TRUE)
```

#### Residential

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 25, "United States", scenario_rename = TRUE)
```

#### Commercial by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 32, "United States", scenario_rename = TRUE)
```

#### Commercial

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 26, "United States", scenario_rename = TRUE)
```

### Industry {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 18, "United States", scenario_rename = TRUE)
```

#### Industry

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 9, "United States", scenario_rename = TRUE)
```

### Transportation {.tabset}

#### Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 19, "United States", scenario_rename = TRUE)
```

#### Transportation

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 12, "United States", scenario_rename = TRUE)
```

### Vehicle Share {.tabset}

#### Sales Share 

```{r}
df1 = data_from_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 33, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Freight")
df2 = data_from_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 34, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Passenger")
df = rbind(df1,df2)

var_palette <- unique(df$model)

ggplot(data = df) +
  geom_line(aes(x=year,y=value, colour = model), size = 1) +
  facet_grid(facet~variable_rename) +
  scale_color_manual(values = c("GCAM" = "#bfef45",
                                'OP-NEMS' = "#000075",
                                'USREP-ReEDS' = "#9a6324")) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent)  +
  labs(title = 'Vehicle Sales Share') +
  theme(
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1),
        panel.spacing.x = unit(4, "mm"))

```

#### Stock Share 

```{r}
df1 = data_from_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 35, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Freight")
df2 = data_from_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 36, "United States", scenario_rename = TRUE) %>%
  mutate(facet = "Passenger")
df = rbind(df1,df2)

ggplot(data = df) +
  geom_line(aes(x=year,y=value, colour = model), size = 1) +
  facet_grid(facet~variable_rename) +
  scale_color_manual(values = c("GCAM" = "#bfef45",
                                'OP-NEMS' = "#000075",
                                'USREP-ReEDS' = "#9a6324")) +
  theme_custom() +
  scale_y_continuous(labels = scales::percent)  +
  labs(title = 'Vehicle Stock Share') +
  theme(
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1),
        panel.spacing.x = unit(4, "mm"))
```

## Percent Electricity

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 14, "United States", scenario_rename = TRUE,
                                  level_var = c("Buildings", "Industry", "Transportation","Total Electricity"))
```


# Supply

## Secondary Energy {.tabset}

### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 8, "United States", scenario_rename = TRUE)
```

### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 25, "United States", scenario_rename = TRUE)
```

### Fuel

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 15, "United States", scenario_rename = TRUE)
```

## Electricity Production 

### Generation {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 15, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
```

#### Model - Zoom

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 27, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Total Electricity"))
```

#### Generation

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 13, "United States", scenario_rename = TRUE)
```

#### Stats

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,13)
figure_subset_vars <- unique(figure_subset_df$variable)
se_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, figure_subset_vars, data_long_clean, config)
se_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity", data_long_clean, config)


se_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Coal", data_long_clean, config)
se_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Gas", data_long_clean, config)
se_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Oil", data_long_clean, config)
se_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Solar", data_long_clean, config)
se_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 13, "Secondary Energy|Electricity|Wind", data_long_clean, config)

```

### Generation Inputs {.tabset}

#### Totals

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 37, "United States", scenario_rename = TRUE)
```

#### w/ and w/o CCS

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 38, "United States", scenario_rename = TRUE)
```

### Capacity {.tabset}

#### Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 16, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
```

#### Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 26, "United States", scenario_rename = TRUE,
                         level_var = c("Coal", "Gas", "Oil","Solar", "Wind", "Storage", "Total Electricity"))
```

#### Capacity

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 3, "United States", scenario_rename = TRUE)
```

#### Stats

```{r}
figure_subset_df <- get_figure_subset_df(figmap_nrgco2_stackbar,3)
figure_subset_vars <- unique(figure_subset_df$variable)
cap_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, figure_subset_vars, data_long_clean, config)

cap_coal_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Coal", data_long_clean, config)
cap_gas_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Gas", data_long_clean, config)
cap_oil_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Oil", data_long_clean, config)
cap_solar_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Solar", data_long_clean, config)
cap_storage_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Storage Capacity", data_long_clean, config)
cap_wind_value_list <- get_value_list_from_var_list(figmap_nrgco2_stackbar, 3, "Capacity|Electricity|Wind", data_long_clean, config)
```

Electricity capacity is estimated to increase from 2020 to 2040:

-   GCAM: `r cap_value_list$GCAM`%
-   OP-NEMS: `r cap_value_list$"OP-NEMS"`%
-   USREP-ReEDS: `r cap_value_list$"USREP-ReEDS"`%

By technology, electricity capacity is estimated to change from 2020 to 2040:

-   Coal:
    -   GCAM: `r cap_coal_value_list$GCAM`%
    -   OP-NEMS: `r cap_coal_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r cap_coal_value_list$"USREP-ReEDS"`%
-   Gas:
    -   GCAM: `r cap_gas_value_list$GCAM`%
    -   OP-NEMS: `r cap_gas_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r cap_gas_value_list$"USREP-ReEDS"`%
-   Oil:
    -   GCAM: `r cap_oil_value_list$GCAM`%
    -   OP-NEMS: `r cap_oil_value_list$"OP-NEMS"`%
-   Solar:
    -   GCAM: `r cap_solar_value_list$GCAM`%
    -   OP-NEMS: `r cap_solar_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r cap_solar_value_list$"USREP-ReEDS"`%
-   Storage:
    -   OP-NEMS: `r cap_storage_value_list$GCAM`%
    -   USREP-ReEDS: `r cap_storage_value_list$"OP-NEMS"`%
-   Wind:
    -   GCAM: `r cap_wind_value_list$GCAM`%
    -   OP-NEMS: `r cap_wind_value_list$"OP-NEMS"`%
    -   USREP-ReEDS: `r cap_wind_value_list$"USREP-ReEDS"`%

## Combustion {.tabset}

### Generation

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 6, "United States", scenario_rename = TRUE)
```

### Generation by Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 20, "United States", scenario_rename = TRUE)
```

### Generation by Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 28, "United States", scenario_rename = TRUE)
```

### Capacity

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 4, "United States", scenario_rename = TRUE)
```

### Capacity by Model

```{r, fig.width=12}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 22, "United States", scenario_rename = TRUE)
```

### Capacity by Model - Zoom

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 29, "United States", scenario_rename = TRUE)
```

## Non-Combustion {.tabset}

### Generation

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 7, "United States", scenario_rename = TRUE)
```

### Generation by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 23, "United States", scenario_rename = TRUE)
```

### Capacity

```{r}
print_graph("stacked_bar", config, data_long_clean, figmap_nrgco2_stackbar, 5, "United States", scenario_rename = TRUE)
```

### Capacity by Model

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 21, "United States", scenario_rename = TRUE)
```

## Primary Energy {.tabset}

### Fossil 

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 6, "United States", scenario_rename = TRUE)
```

### Non-Fossil

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 7, "United States", scenario_rename = TRUE)
```

------------------------------------------------------------------------

# Model Comparision

## Reference Model: {.tabset}

### GCAM

```{r}
print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 23, "United States", scenario_rename = TRUE)
```

### OP-NEMS

```{r}
print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 25, "United States", scenario_rename = TRUE)
```

### USREP-ReEDS

```{r}
print_graph("diff_bar", config, data_long_clean, figmap_nrgco2_diffbar, 24, "United States", scenario_rename = TRUE)
```

## Input Assumptions {.tabset}

### Population

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 12, "United States", scenario_rename = TRUE)
```

### GDP

```{r}
print_graph("time_series", config, data_long_clean, figmap_nrgco2_timeseries, 13, "United States", scenario_rename = TRUE)
```

